---
title: "Individual Plots"
#subtitle: "Season 2023"
author: "~"
date: "`r Sys.Date()`"
toc: false
toc_depth: 1
classoption: a4paper
#documentclass: cricalm
documentclass: article
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#source("get-data.R")
#source("../parse-raw-data.R", local = knitr::knit_global())
#load("./data/*")
library(readr)
Zclub <- read_csv("data/Zclub.csv", col_types = cols(...1 = col_skip()))
#load("./data/EbatAvgTY")
#load("./data/BbatAvg")
load("./data/Bbatting")
#load("./data/EbowlAvgTY")
#load("./data/BbowlAvg")
load("./data/Bbowling")
load("./data/Bdates")
#load("./data/Bfielding")
#load("./data/Binningses")
#load("./data/Ematches")
#load("./data/Bmatches")
load("./data/Eplayers")
#load("./data/EplayersNC")

## load the config
library(yaml)
conf <- yaml.load_file("./config/config.yaml")
#conf$club_of_interest_name <- D.club$name[D.club$id== conf$club_of_interest] # this isn't neat, so just set it by hand in the yaml
# load other packages
library(tidyr)
library(dplyr)
library(kableExtra)
library(ggplot2)
library(lubridate)
#library(dplR) # provides latexify, need this for club names containing \&

# get the subject's name
player_name <- as.character(E.players %>% filter(player_id==conf$player_to_plot) %>% 
                              slice_head(n=1) %>% select("Name"))

thisbatterty <- B.batting %>% filter(!is.na(Runs), batsman_id==conf$player_to_plot,
                                   Yr == conf$year_of_interest)

numbatsty <- nrow(thisbatterty)

thisbatter <- B.batting %>% filter(!is.na(Runs), batsman_id==conf$player_to_plot)

numbats <- nrow(thisbatter)

thisbowlerty <- B.bowling %>% filter(!is.na(O), bowler_id==conf$player_to_plot,
                                     Yr == conf$year_of_interest)
numbowlsty <- nrow(thisbowlerty)
thisbowler <- B.bowling %>% filter(!is.na(O), bowler_id==conf$player_to_plot)
numbowls <- nrow(thisbowler)


H.heatherAv <- c("Season", "Avg", "Matches", "Wkts")
H.F.plain <- function(x, this_caption, flower) x %>%  
  select(all_of(flower)) %>% 
  kbl(longtable = T, booktabs = T, row.names = F, caption = this_caption) %>%
  kable_styling(latex_options = c("repeat_header", "striped", "hold_position"),
                font_size = 7) 


# a function to round averages
avRn <- function(x) trunc(x*100, signif=2 )/100

```

`r paste("# Report for", player_name)`

## Batting

`r paste("For", numbatsty, "innings this year and", numbats, "in all")`

### Generally
```{r mainBat, echo=FALSE}
plot2 <- thisbatter %>%   ggplot(aes(y=Runs, 
                                     na.rm = TRUE)) + geom_histogram(binwidth = 5) +
  geom_boxplot() +
  coord_flip() +
  #theme(axis.title.y=element_blank(),axis.text.y=element_blank(),axis.ticks.y=element_blank() )+ 
  labs(title = paste("All-time") )

plot(plot2)


```

### Day of week
```{r bat-dow, echo=FALSE}
plot1 <- thisbatterty %>%
  ggplot(aes(x=actuallyDate, y=Runs, col = wday(actuallyDate, label=TRUE), 
             na.rm = TRUE)) + geom_point() +
            labs(title = paste("Scores this year"),
                 x="Date",
                 col = "Day of week")

plot2 <- thisbatterty %>%
  ggplot(aes(x=wday(actuallyDate, label=TRUE), y=Runs, col = `How Out`, shape=Ven,
             na.rm = TRUE)) + geom_point(size=2) +
            labs(title = paste("Scores this year"),
                 x="Day of week",
                 shape= "Venue",
                 col = "How Out")

# plot3 <- thisbatterty %>%   ggplot(aes(x=wday(actuallyDate, label=TRUE), y=Runs, 
#              na.rm = TRUE))  +
#               labs(title = paste("Scores this year"),
#                  x="Day of week")

plot4 <- thisbatter %>%   ggplot(aes(x=wday(actuallyDate, label=TRUE), y=Runs, 
             na.rm = TRUE)) + geom_boxplot() +
             geom_dotplot(binaxis = "y", stackdir='center', dotsize=1,  binwidth = 1) +
              labs(title = paste("All-time"),
                 x="Day of week")

plot(plot1)

plot(plot2)

#plot(plot3)

plot(plot4)

```

### Venues


```{r bat-ground, echo=FALSE}
plot1 <- thisbatterty %>%
  ggplot(aes(x=actuallyDate, y=Runs, col = Ven, 
             na.rm = TRUE)) + geom_point() +
            labs(title = paste("Scores this year"),
                 x="Date",
                 col = "Venue")


plot2 <- thisbatter %>%
  ggplot(aes(x=actuallyDate, y=Runs, col = Ven, 
             na.rm = TRUE)) + geom_point() +
            labs(title = paste("Scores, all time"),
                 x="Date",
                 col = "Venue")


plot4 <- thisbatter %>%   ggplot(aes(x=Ven, y=Runs, 
             na.rm = TRUE)) + geom_boxplot() +
             geom_dotplot(binaxis = "y", stackdir='center', dotsize=1,  binwidth = 1) +
              labs(title = paste("All-time"),
                 x="Venue")

plot(plot1)

plot(plot2)

plot(plot4)

```


### Match type

```{r bat-type, echo=FALSE}
plot1 <- thisbatterty %>%
  ggplot(aes(x=actuallyDate, y=Runs, col = Type, 
             na.rm = TRUE)) + geom_point() +
            labs(title = paste("Scores this year"),
                 x="Date",
                 col = "Type")


plot2 <- thisbatter %>%
  ggplot(aes(x=actuallyDate, y=Runs, col = Type, 
             na.rm = TRUE)) + geom_point() +
            labs(title = paste("Scores, all time"),
                 x="Date",
                 col = "Type")


plot4 <- thisbatter %>%   ggplot(aes(x=Type, y=Runs, 
             na.rm = TRUE)) + geom_boxplot() +
             geom_dotplot(binaxis = "y", stackdir='center', dotsize=1,  binwidth = 1) +
              labs(title = paste("All-time"),
                 x="Type")

plot(plot1)

plot(plot2)

plot(plot4)

```


### How Out
```{r bat-howout, echo=FALSE}
plot1 <- thisbatter %>%
  ggplot(aes(x=`How Out`, y=Runs, col = Yr, 
             na.rm = TRUE)) + geom_point() +
            labs(title = paste("Scores"),
                 x="How Out",
                 col = "Year")

plot(plot1)


plot2 <- thisbatterty %>%
  ggplot(aes(x=`How Out`, fill = `How Out`,
             na.rm = TRUE)) + geom_bar(position = "stack") +
  labs(title = paste("Dismissals this year"),
       x="How Out",
       y="Count"
       )

plot(plot2)

plot3 <- thisbatter %>%
  ggplot(aes(x=`How Out`, fill = `How Out`,
             na.rm = TRUE)) + geom_bar(position = "stack") +
  labs(title = paste("Dismissals all time"),
       x="How Out",
       y="Count"
       )

plot(plot3)

```

### Playing XI

```{r bat-xi, echo=FALSE}
plot1 <- thisbatterty %>%
  ggplot(aes(x=actuallyDate, y=Runs, col = `Batting Side`, 
             na.rm = TRUE)) + geom_point() +
            labs(title = paste("Scores this year"),
                 x="Date",
                 col = "Venue")


plot2 <- thisbatter %>%
  ggplot(aes(x=actuallyDate, y=Runs, col = `Batting Side`, 
             na.rm = TRUE)) + geom_point() +
            labs(title = paste("Scores, all time"),
                 x="Date",
                 col = "Venue")


plot4 <- thisbatter %>%   ggplot(aes(x=`Batting Side`, y=Runs, 
             na.rm = TRUE)) + geom_boxplot() +
             geom_dotplot(binaxis = "y", stackdir='center', dotsize=1,  binwidth = 1) +
              labs(title = paste("All-time"),
                 x="Venue")

plot(plot1)

plot(plot2)

plot(plot4)

```



## Bowling

```{r bowl-gen, echo=FALSE, warning=FALSE}
plot <- thisbowler %>%   ggplot(aes(x = as.factor(W), y= R, col=Ven, fill=Ven,
                                     na.rm = TRUE)) + geom_boxplot() +
  #geom_dotplot(binaxis = "y", stackdir='center', dotsize=1,  binwidth = 1, position = "dodge") +
  labs(title = paste("All-time"),
       x = "Wickets",
       y = "Runs")



plot(plot)

plot1 <- thisbowler %>%   ggplot(aes(x = actuallyDate, y=W, 
                                    col = Ven, 
                                    na.rm = TRUE)) + geom_point() +
  #geom_dotplot(binaxis = "y", stackdir='center', dotsize=1,  binwidth = 1, position = "dodge") +
  labs(title = paste("All-time"),
       x = "Date",
       y = "Wickets")

plot2 <- thisbowlerty %>%   ggplot(aes(x = actuallyDate, y=W, 
                                    col = Ven, 
                                    na.rm = TRUE)) + geom_point() +
  #geom_dotplot(binaxis = "y", stackdir='center', dotsize=1,  binwidth = 1, position = "dodge") +
  labs(title = paste("This year"),
       x = "Date",
       y = "Wickets")

plot3 <- thisbowler %>%   ggplot(aes(x = actuallyDate, y=as.numeric(Avg), 
                                     col = Ven, 
                                     na.rm = TRUE)) + geom_point() +
  #geom_dotplot(binaxis = "y", stackdir='center', dotsize=1,  binwidth = 1, position = "dodge") +
  labs(title = paste("All-time"),
       x = "Date",
       y = "Average")

plot4 <- thisbowlerty %>%   ggplot(aes(x = actuallyDate, y=as.numeric(Avg), 
                                     col = Ven, 
                                     na.rm = TRUE)) + geom_point() +
  #geom_dotplot(binaxis = "y", stackdir='center', dotsize=1,  binwidth = 1, position = "dodge") +
  labs(title = paste("Averages, this year"),
       x = "Date",
       y = "Average")


plot(plot1)

plot(plot2)

plot(plot3)

plot(plot4)


```

## Bowling stats by season
```{r bowl-stats}

B.bowling %>% filter(bowler_id == conf$player_to_plot) %>%
  group_by(Yr) %>% 
  summarise(`Avg` = avRn(sum(R)/sum(W)), `Matches` = n(), Wkts = sum(W)) %>% ungroup() %>%
  rename(Season = Yr) %>%
  arrange(desc(Season)) %>% 
  H.F.plain("Bowling stats by season", H.heatherAv)

```
# Setup

## Date ranges
Data collected from Play-Cricket. 
For `r conf$club_name`, from `r B.dates$our_earliest` to `r B.dates$our_latest`,
n=`r B.dates$count_us`.  For all matches, from `r B.dates$all_earliest` to
`r B.dates$all_latest`, n=`r B.dates$count_all`.

