---
title: "Quiz"
#output: beamer_presentation
classoption: a4paper
documentclass: article
output:
  pdf_document: default
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(kableExtra)
library(scales)
source("displayFuncs.R")
source("headers-def.R")
source("avgFuncs.R")

load("./data/parsed.RData") #load in prepared data

```

## Premise

- All drawn from play-cricket in mid-September
- Individual stats only for Milton games, not other clubs by our players
- Inclusion of non-Milton games is patchy

```{r individstats}
#generate a table of individuals' averages etc

#some names of interesting people
#this is kludged on names not ids #TODO fix

R.interesting_people <- c("JOhn Xavier", "Nicholas Widdowson", "David Gibson",
                          "Jay Dann", "Nathan Sivajoti","Mark Barton", 
                          "Alex McPherson", "Joe Jones", "William Jupp",
                          "Chris Day", "Will Day", "Edward Pinches",
                          "Thomas Holroyd", "Adam Roberts", "Philip Allen")
# batting averages etc
Z.nicebatavgs <- F.batavg.us |> filter(Name %in% R.interesting_people) |> 
  select(Name, Runs, `Ìnnings batted`= Inns, `Batting average`= Avg, 
         `Highest score` = HSraw, `Batting SR` = SR, `Catches` = Ct)

# bowling avgs
Z.nicebowlavgs <- F.bowlavg.us |> filter(Name %in% R.interesting_people) |> 
  select(Name, `Wickets` = W, `Bowling average`= Avg, `Economy` = Econ, 
         `Bowling SR` = SR, `5wi`)

#lengthen, bind, drop zero values
Z.batavgslong <- Z.nicebatavgs |> pivot_longer(!Name, names_to="Stat", values_to = "Value")
Z.bowlavglong <- Z.nicebowlavgs |> pivot_longer(!Name, names_to="Stat", values_to = "Value")

Z.playerstats <- bind_rows(Z.batavgslong, Z.bowlavglong) |> 
  filter_out(Value == 0)

# bin into similar-values ##TODO consider whether automate generting of breaks
Z.playerstats <- Z.playerstats |> mutate(
  bin = cut(Value, breaks= c(-Inf,10,30,50,250,Inf), 
            labels=c("XS", "S", "M", "L", "XL"))
) 

#TODO tidy formatting esp for integer values
#TODO pretty beamer slides with suitable reveals

```

## Samples of player data
```{r sampling-def}
# define a function to pull a sample

samplepull <- function(df, size="M", number=6) {df %>%
    filter(bin==size) |> slice_sample(n=number) |> select(-bin)
}

```

### Very small numbers
```{r xs-samples}
Z.roundi <- Z.playerstats |> samplepull(size="XS") 

Z.roundi |> kable()

```

### Small numbers
```{r s-samples}
Z.roundii <- Z.playerstats |> samplepull(size="S") 

Z.roundii |> kable()

```

### Medium numbers

```{r m-samples}
Z.roundiii <- Z.playerstats |> samplepull(size="M") 

Z.roundiii |> kable()

```

### Large numbers

```{r l-samples}
Z.roundiv <- Z.playerstats |> samplepull(size="L") 

Z.roundiv |> kable()

```

### Very large numbers
```{r xl-samples}
Z.roundv <- Z.playerstats |> samplepull(size="XL") 

Z.roundv |> kable()

```

## Whole table of player data
```{r all-player-data}
Z.playerstats %>% arrange(Value) %>% kable()

```

```{r clubstats}
# ideas:
#career:
# Most runs
# Highest batting average
# Highest batting strike rate
# Most wickets
# Lowest bowling strike rate
# Lowest bowling average
# Lowest bowling economy

#% wins in a year
# count of days with three league wins
# record totals: for, against, not-out, at each ground

```

## Club totals

Record highest, record lowest, and median totals; by:
 *  whether we bat or field,
 *  venue: Sycamores, North Lodge, or other,
 *  whether or not we win
 
```{r record-totals}

  F.inningses.circle |> 
  drop_na(Total, us_batting, Place) |> 
  filter(result_club %in% c('W', 'L'), Total > 0, `Inns of match`==1) |>
  summarise(.by= c(us_batting, Place, result_club),
            Highest = max(Total),
            Lowest = min(Total),
            Avg = as.integer(floor(median(Total)))) |> 
  arrange(desc(Avg)) |> 
  mutate(
    us_batting = us_batting |> 
      recode_values( TRUE ~ "Milton batting",
                     FALSE ~ "Milton fielding")) |> 
  rename(`Our Result` = result_club,
         `Our Role` = us_batting) |> kable()
```

