---
title: "Milton Cricketers' Almanack"
subtitle: "Season 2024"
author: "Niall Taylor"
# date: "`r Sys.Date()`"
date: "April 2025"
toc: true
toc_depth: 1
classoption: a4paper
documentclass: cricalm
#documentclass: report
output:
  pdf_document: default
header-includes:
   - \usepackage{tabularx}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
setwd("../")
source("parse-tidy.R")
source("displayFuncs.R")

## load the config
library(yaml)
conf <- yaml.load_file("config/config.yaml")
#conf$club_of_interest_name <- D.club$name[D.club$id== conf$club_of_interest] # this isn't neat, so just set it by hand in the yaml

# load other packages
library(tidyverse)
library(kableExtra)
library(lubridate)
#library(dplR) # provides latexify, need this for club names containing \&

# check the year of interest is sensible
if (nrow(B.matches %>% filter(Yr == conf$year_of_interest)) == 0){
  stop("ERROR: No data in year of interest.")}

## a default size
dfsz <- 7

## Configure some heading sets for nice display

 #H.cyclamen <-  c("Name", "O", "M", "R", "W",  "Date", "Team", "Batting Club", "Ground")

H.F.cyclamen <- function(x, this_caption, flower) x %>%    select(all_of(flower)) %>% 
  kbl(longtable = T, booktabs = T, row.names = F, caption = this_caption) %>%
  kable_styling(latex_options = c("repeat_header", "striped", "hold_position"), font_size = dfsz) %>%
  column_spec(1, width = "10em") %>%
  column_spec(6:7, width = "6em") %>%
  column_spec(8:9, width = "9em")

#  H.dianthus  <- c("Team", "Score", "Ovs", "Date", "Fielding Side", "Ground")
# H.rudbeckia <- c("Team", "Score", "Ovs", "Date", "Fielding Side", "Extras")
# H.wolfsbane <- c("Team", "Score", "Ovs", "Date", "Fielding Team", "Byes")
# H.peony  <- c("Fielding Side", "Score", "Ovs", "Date", "Batting Side", "Bowlers")
H.F.dianthusfam <- function(x, this_caption, flower) x %>% select(all_of(flower)) %>%
  kbl(longtable = T, booktabs = T, row.names = F, caption = this_caption) %>%
  kable_styling(latex_options = c("repeat_header", "striped", "hold_position"), font_size = dfsz) %>%
  column_spec(1, width = "10em") %>%
   column_spec(4, width = "6em") %>%
    column_spec(5:6, width = "10em")
 
 
#H.freesia   <- c("Home Club", "Away Club", "Date", "Ground", "Match Aggregate", "Match Overs")
H.F.freesia <- function(x, this_caption, flower) x %>% select(all_of(flower)) %>%
  kbl(longtable = T, booktabs = T, row.names = F,   caption = this_caption) %>%
  kable_styling(latex_options = c("repeat_header", "striped", "hold_position"), font_size = dfsz) %>%
  column_spec(1:2, width = "10em") %>%
  column_spec(3, width = "6em") %>%
  column_spec(4, width = "9em")

# #H.violet <- c("Match Summary", "Date",
#                 "Ground", 
#                "Name", "Runs", "Balls", 
#                "Analy", "Ct", "Std") 
H.F.violetfam <- function(x, this_caption, flower) x %>%    select(all_of(flower)) %>% 
  kbl(longtable = T, booktabs = T, row.names = F, caption = this_caption) %>%
  kable_styling(latex_options = c("repeat_header", "striped", "hold_position"), font_size = dfsz) %>%
  column_spec(1, width = "12em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3:4, width = "9em")

#H.lily <-        c("Name", "Runs", "Balls", "Date", "Team", "Fielding Club", "Ground",       "Res") # now two short of the rest of the family
# H.hibiscus <-    c("Name", "Runs", "Balls", "Date", "Fielding Club", "Ground", "4", "6")
# H.safflower <-   c("Name", "Runs", "Balls", "Date", "Fielding Club", "Ground", "How Out") 
# H.thistle <-     c("Name", "Runs", "Balls", "Date", "Fielding Club", "Opposition Score", "Contrib")

H.F.lilyfam <- function(x, this_caption, flower) x %>% select(all_of(flower)) %>% 
  kbl(longtable = T, booktabs = T, row.names = F, caption = this_caption) %>%
  kable_styling(latex_options = c("repeat_header", "striped", "hold_position"), 
                font_size = dfsz)  %>% 
  column_spec(1, width = "9em") %>%
  #column_spec(2:3, width = "0.15cm") %>%
  column_spec(5, width = "6em") %>%
    column_spec(6:8, width = "9em") 

# H.hyacinth <- c("Match Summary", "Date", "Result")
H.F.hyacinthfam <- function(x, this_caption, flower) x %>% select(all_of(flower)) %>%
  kbl(longtable = T, booktabs = T, row.names = F,   caption = this_caption) %>%
  kable_styling(latex_options = c("repeat_header", "striped", "hold_position"), font_size = dfsz) %>%
  column_spec(1, width = "25em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "12em")

H.F.phloxfam <- function(x, this_caption, flower) x %>% select(all_of(flower)) %>%
  kbl(longtable = T, booktabs = T, row.names = F,   caption = this_caption) %>%
  kable_styling(latex_options = c("repeat_header", "striped", "hold_position"), font_size = dfsz) %>%
  column_spec(1, width = "20em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "9em") %>%
  column_spec(5, width = "9em")

# H.primrose <- c("Date", "Batting Team", "Fielding Side", "Wkt", "Partnership", "Batter Out", "Batter Rem", "Ven")
# H.periwinkle <- c("Date", "Batting Team", "Fielding Side", "Wkt", "Partnership", "Batter Out", "Batter Rem", 
#                   "Score", "Oppo Score")
H.F.primrosefam <- function(x, this_caption, flower) x %>% select(all_of(flower)) %>%
  kbl(longtable = T, booktabs = T, row.names = F,   caption = this_caption) %>%
  kable_styling(latex_options = c("repeat_header", "striped", "hold_position"), font_size = dfsz) %>%
  column_spec(1, width = "6em") %>%
  column_spec(2:3, width = "9em") %>%
  column_spec(6:7, width = "9em") 



# plain display-ing things
#H.aster <-     c("Name", "Runs", "Inns", "NO", "Avg", "HS", "SR", "50", "100", "Ct", "Std", "RO")
# #H.clematis <-  c("Name", "O", "M", "R", "W", "5wi", "Avg", "Econ", "SR", "Best")
# H.crocosmia <-   c("Name", "M", "Ct", "Std", "RO", "Dis/Inns")
# H.mugwort <- c("Name", "n")
# H.mimosa <- c("Name", "n", "Innings")
# H.yarrow <- c("Season", "Name", "Matches")
# H.heather <- c("Season", "Name", "Total", "Matches")
# H.heatherAv <- c("Season", "Name", "Avg", "Matches", "Wkts")
H.F.plain <- function(x, this_caption, flower) x %>%  
  select(all_of(flower)) %>% 
  kbl(longtable = T, booktabs = T, row.names = F, caption = this_caption) %>%
  kable_styling(latex_options = c("repeat_header", "striped", "hold_position"),
                font_size = dfsz) 

H.F.plainALL <- function(x, this_caption) x %>%  
  kbl(longtable = T, booktabs = T, row.names = F, caption = this_caption) %>%
  kable_styling(latex_options = c("repeat_header", "striped", "hold_position"),
                font_size = dfsz) 

```


\newpage

\setlength{\tabcolsep}{2pt}


# Awards

```{=latex}
\begin{tabular}{ll}
Club person of the year & Jay Dann \\ [2ex]

Most runs &  Joe Jones  \\
Highest score & Sam Jones \\
Most wickets & Sam Jones \\
Best bowling & Tom Holroyd \\
%Best fielder & ~~ \\ 
\end{tabular}
```

## 1st XI


```{=latex}
\begin{tabular}{ll}
Player of the year & John Xavier  \\
Batter of the year & Will Conlon   \\
Bowler of the year & Shyam Perisetla \\
\end{tabular}

\smallskip

\emph{By John Xavier, 1st XI Captain}

The 1s had a strong start, winning four at the start of the season
and then a tough string of five losses. Motivation was kept up with a
curry night, which helped to regroup. Good availability
saw us finishing fourth.
Away at Cambourne we made 136 and despite Hendy taking 3/19 and having
the opposition 95/9, they clung on to reach the target. A few more 
losses inspired a tight win, bowling out St Giles in the 44th over with 
four runs to spare.

Thanks to vice-captains for their work.

Performances with the bat, Will Conlon made a century and a 93 but out 
to a poor shot. Sandesh made a 90, Nick 69 and Nath 65. Bowling, John 
took 5/21 and Mark 4/19.

```

## 2nd XI

```{=latex}

\begin{tabular}{ll}
Player of the year & Rakesh Panigrahi  \\
Batter of the year & Joe Jones \\
Bowler of the year & Zubair Akbar \\
Captain's Impact Player Award & Harsha Mallesh \\
\end{tabular}

\smallskip

\emph{By Rakesh Panigrahi, 2nd XI Captain}

First of all congratulation to all team members for getting promoted to 
J2, well done everyone and it was great for me as a captain when you have
match winners in the team. It makes the job a little easier. 


We could have won the league if the rain god had been in our favour and 
we played a little better against Longstowe. But overall it's a year, 
being no 2 in the table is a great achievement and congratulations 
again.


The would not have been possible without some dynamic performances from 
two players, Joe Jones and Zubair Akbar. Joe for having a dream run this 
season scoring 567 runs at 81.00 and seven 50s. He was top run getting 
in the league as well. Zubair was lethal in his bowling taking 23 
wickets with an average just below 12. That's just incredible. And he 
was the second-highest wicket taken in the league as well.


Ed Pinches for taking the highest number of catches, 7 with some 
spectacular catches on the boundary line. And special thank you to 
Pinches for helping me out, on and off the field, whenever I need him.


I would like to thank the captains of 1st and 3rd team for helping me 
getting a best team with the availability. You played part in getting 
2s promoted as well. And to Nath and Jimmy for helping us win the last 
game of the season.

Harsha always performed when 
the team needed him, whether it's batting or bowling. His contributions 
helped us win some crucial games. 


Thank you for voting for me as player of the year. I would like to 
dedicate the award to my team, without them this would not have been 
possible.

```

## 3rd XI
```{=latex}

\begin{tabular}{ll}
Player of the year & Alex McPherson \\
Batter of the year & Robin Nelder \\
Bowler of the year & Jamie McPherson  \\
\end{tabular}

\smallskip

\emph{By Tom Holroyd, 3rd XI Captain}

Good availability this year, and an encouraging season.
Thanks to Rakesh for his recruitment
work. With young players showing improvement, and more experience 
overall, their contribution was strong. Promotion to J4W has been 
confirmed. It is much
nicer to play not expecting to lose: we had many games this year which
were close but didn't go our way. We took eight wickets against Over \&
Willingham having made just 53. At March chasing 85, Andy Staplehurst's
35 not out helped us over the line. Also with the bat, Tom Hingston's
45 against Longstanton helped set a total we could defend. Bowling
highlights were Holroyd's 6/32 and Katie Gibson 5/21. Alex McPherson
stood out in the field, and a particular thanks here to all who kept
wicket.


```


## Special Awards
```{=latex}
\emph{By Will Day, Secretary Emeritus}

(something about Rakesh's umpiring -- @Will was this the bit to cut? I 
didn't get it anyway)

\subsubsection*{The Mark Barton Availability Award for Bravery in the Face of Relatives}
\textbf{Nathan Sivajoti}, who despite becoming a father and warning
he would not be around much, played almost every weekend, several 
midweek, and went on
tour twice.

\subsubsection*{The James Drummond award for biggest junior league bully}
In third, Joe Jones, for moving to Australia. In second, Sam Jones at
Reach, hitting 116 in a friendly. The winner is \textbf{Zack Smith}, 
for 256 at 18.29 and getting the 2s thrown out of the cup for being 
too good.


\subsubsection*{Most ducks}
Third: Sam Jones. Second: Adam Roberts. First: \textbf{Phil Allen}, 
with eight.

\subsubsection*{The I Told You So Award}
\textbf{Joe Jones}, who is reportedly now opening the bowling in 
Australia.


%EDITOR -- ADD IN 
%~ \subsubsection*{A note from the Editor}
%~ \textit{
%~ An additional award has been created. The `Will Day 
%~ ``Fuck It, That'll Do'' MVP Award for Embracing Minimal Viable Product'
%~ celebrates borderline adequacy, just about phoning it in, and 
%~ eliminating waste in cricket administration. The inaugural winner is 
%~ Will Day, for delivering a series of entertaining mild insults dressed 
%~ up as awards, which were not at all obviously written that afternoon, 
%~ and handing out kinder eggs for all his prizes under a guise of 
%~ thoughtful planning, not that the multipack was on offer in Tesco.}

```

\newpage 

# Almanack: `r conf$club_name`

\setlength{\tabcolsep}{3pt}

## A statistical vignette
*By Niall Taylor *

As ever, my data source is play-cricket. If that is wrong, then
what I am about to say is wrong, too.


### Centuries

\begin{tabular}{llll}
116 & Sam Jones & Friendly XI vs Reach & 11 Aug 2024 \\
104* & Will Conlon & 1st XI vs Linton & 18 May 2024 \\
101* & Sam Jones & 3rd XI vs Cambourne & 20 Jul 2024 \\
\end{tabular}

\medskip

Sam's 116 came in a friendly and is the highest score in friendlies, 
beating Nick Widdowson's 2021 record by 22, but did not win the match. 
It came from 100 balls, and a team total of 176. No other batter in 
that match made double figures, there were 25 extras. His contribution 
is a mere 65.9\%, the fourth highest proportion on record for Milton 
but short of the Bannerman\footnote{At which match, one Jupp made 63 
off 241 balls, SR 26.14; then 0 \& 1 as opener in the Second Test.}.

\smallskip

His 101* is now the eleventh century for the 3rd XI; in that match he 
took three catches, a rare -- possibly unique -- double.

\smallskip

In May, a
104* for Will Conlon, some way off his own record for the 1st XI.


### Other batting

As well as the centurions, eighteen batters made at least one fifty, 
with Joe making a record seven in the year. Both Will and Nath 
twice made fifty in matches Milton lost.

There were 37 scores between 50 and 100 (2023: 24; 2022: 35).

Strike rates: excluding some lower scores (Zubair Ikram 12 off 4), Will 
Jupp's 19 off 9 (211.11) against TAC, is up there with Ani Ghosh 15 off 
7 (214.29) against Fen Ditton, and Sam Jones 101 came from 38 (265.79).

On the other end, Zack's 10 from 41 against St Giles
ranks among the most balls faced for score of ten or less.

The Midweek team against NCI on 4 June had the rare incident of all
players either making 10 or more, or not batting at all\footnote{So we
had everyone in double figures, cf vs Reach, where no-one was}.

In a similar but less good way, Northstowe on 4 May made 91 to win
with the top scoring batter on 15.

### Noteable partnerships

The partnership between Joe Jones and Rakesh against Longstowe in May, 
at 162 for the second wicket is, for any wicket, the highest recorded 
for the 2nd XI and sixth highest overall. 

Pradeep and Sandesh made an opening 138 for 2nd XI at Stapleford, fifth 
highest for that wicket.

Joe and Pinches made 136 also for the second wicket, which is the 
fourth highest for that wicket.

Jay and Nick made 59 against Saffron Walden, fourth highest for the 
eighth wicket.

Back in April, Will Day and David Gibson were denied, by one run at 
47*, a record-equalling eighth wicket stand in friendlies\footnote{This 
is rather shaky, retirements are common and distort the picture}. 

\medskip

\noindent
\begin{tabularx}{0.95\textwidth}[h]{lllXl}
162  & 2nd & J Jones \& R Panigrahi     & 2nd XI vs Longstowe & 25 May 2024\\
138  & 1st & P Gowda \& S Dambekodi    & 2nd XI vs Stapleford & 	08 Jun 2024 \\
136  & 2nd & J Jones \& E Pinches & 2nd XI vs Northstowe & 	27 Jul 2024 \\	
122* & 3rd & J Jones \& H Mallesh & 2nd XI vs Stapleford & 	13 Jul 2024 \\	
103  & 4th & P Kumar \& J Xavier       & 1st XI vs Wilbrahams & 	17 Aug 2024 \\	
101  & 2nd & J Jones \& R Panigrahi    & 2nd XI vs Steeple Morden &	29 Jun 2024 \\	
94   & 2nd & P Kumar \& C Day 	       & 2nd XI vs Barrington & 03 Aug 2024 \\	
\end{tabularx}
\medskip


### Bowling

W Day with 2-2-0-3 in the internal friendly joins a short list of those 
to take wickets for no runs.

T Holroyd 6 for 32 on 31 August against Ramsey is the eighth best 
analysis on record and the best in competitive games since 2015. 
Milton still lost; this is the best analysis in a game lost at home.

There were sixteen four-fors (2023: 12; 2022: 11):

\medskip

\noindent
\begin{tabularx}{0.95\textwidth}[h]{llXl}

6/32 &	Thomas Holroyd 	& 3rd XI vs Ramsey &	31 Aug 2024 \\
5/21 &	John Xavier 	& 1st XI vs Cambridge St. Giles & 	27 Jul 2024 \\
5/21 & 	Katie Gibson 	& 3rd XI vs Wisbech Town & 25 May 2024 \\
5/39 &	Zubair Akbar 	& 2nd XI vs Madingley & 	18 May 2024 \\
4/5  &	Stephen Dye 	& 3rd XI vs Over and Willingham & 17 Aug 2024 \\
4/10 &	Jamie McPherson & 3rd XI vs March Town & 	15 Jun 2024 \\
4/15 &	Rahul Pillai 	& 2nd XI vs Barrington & 	03 Aug 2024 \\
4/16 &	David Gibson 	& 2nd XI vs Fen Ditton &	01 Jun 2024 \\
4/19 &	Harsha Mallesh 	& 2nd XI vs TAC &  	22 Jun 2024 \\
4/19 &	Mark Barton 	& 1st XI vs Chatteris &	04 May 2024 \\
4/24 &	Keshav Rattan 	& 3rd XI vs Longstanton Grasshoppers & 22 Jun 2024 \\
4/27 &	Shyam Perisetla & 1st XI vs Madingley  & 10 Aug 2024 \\
4/28 &	Rakesh Panigrahi 	& 2nd XI vs   Stapleford & 08 Jun 2024 \\
4/29 &	Jamie McPherson 	& 3rd XI vs   Burwell \& Exning & 	08 Jun 2024 \\
4/31 &	William Robinson 	& 2nd XI vs   Longstowe  & 25 May 2024 \\
4/35 &	Zubair Akbar 	& 2nd XI vs Steeple Morden &	11 May 2024\\


\end{tabularx}



\medskip

At Saffron Walden on 25 May, our 1st XI bowlers shared the spoils, a
rare occurrence of every bowler taking at least two. 

There was sharing too 
against Madingley on 22 June: despite conceding 264, the plan of using
nine bowlers meant no-one went for more than 50, the 3rd XI doing the
same for Eaton Socon on 18 May.

Drummond overwintered on a hat trick and opened his year with a dot.


### Wicket-keeping

\noindent
\begin{tabular}{lll}

Robin Nelder & 8ct, 1 std & plus 3 outfield catches \\
Will Day     & 4ct, 4 std &  	~~''~~ 4~~~~~~~       ''	and one run out\\
William Conlon 	& 8ct       &  	~~      	\\
Sandesh Dambekodi & 4ct, 1std     &   ~~''~~ 4~~~~~~~      '' and two run outs\\
Phillip Allen 	    & 1ct, 3std       & 	~~''~~ 2~~~~~~~      ''	\\


\end{tabular}

\medskip

All of Sandesh's w-k dismissals this year came in the same match, 
against Wilbrahams on 17 August. He also effected one run out in that 
match. This is only the second instance on record of five 
wicket-keeping dismissals in an innings, the other being Dye (3ct, 
2std, 0ro) on 28 May 2016.

All of Phil's w-k dismissals this year came in the same match, against
Ramsey on 31 August. This was the first instance of
four wicket-keeping dismissals for a fortnight, and the only instance 
recorded at North Lodge.

Three of Conlon's catches were in the same innings, 10 August 
vs Madingley.


Conlon (52, 41ct/11std) remains third in all-time wicket-keeping 
wickets; Day (50, 37ct/13std) remains fourth. O'Kane (55, 43ct/12std)
is second, for now.


### Fielding


Alex McPherson took eleven catches in the field. Pete While took ten.
John Xavier, Jay Dann, Nathan Sivajoti each took nine, Chris Goodall
eight.

As a club, there were 178 catches taken
by 36 fielders. (2023: 121 by 30; 2022: 98 by 26; all in addition
to wicket-keeping catches)

Run outs: as last year, I have not included here, as data tend to be 
incomplete.

Fielders took three catches in an innings five times: John Xavier,
 Sam Jones, Ed Pinches, Tom Sharrock and Alex McPherson.




### Others


The most runs
scored by the club in a single day this year was 606 on 27 July, 
fourteenth in the
list of daily totals. (2023-07-08: 578, 28th; 2022-07-23: 887, 1st)

In the year, play-cricket (and my records) has:

- seventeen primaries for thirteen Milton players (2023: 16; 2022: 11; 2021: 20), of which three came on the same day
-  three Milton players dismissed without facing (2023 1; 2022: nil, 2021: 2)
-  24 dropped and 28 missed catches (totals: 2023: 15; 2022: 19)
-  12 half-chances (2023: 13; 2022: 23)
-  five missed run outs or stumpings
-  no recorded instance of hit in the lower abdomen (2023: nil)
-  one bowler falling over and nearly into the non-striker

### Notes


Last year I closed my remarks hoping for a change of fortunes. My 
friends, what a change. The performances on the field, and the 
atmosphere off it showed that we are back, baby, where we belong, 
squarely in the top half or even top third of things.

The weather took its share, and I'd like to think we are getting a 
reputation for trying to get a game on. On a couple of occasions we 
were narrowly denied an opportunity to play a side burdened by their 
own negativity.

We host a good party, don't we? I greatly enjoyed the club day with 
friends old and new, my thanks to all who organised. I also record my 
gratitude to Nath for organising two tours, one with rather more 
activity than the other.

I will let the captains lead on the actual cricket, though if I may 
mention a few things still in my mind? Sandesh took an 
\emph{astonishing} catch at Cambourne, running round to deep mid-wicket 
from, I think, somewhere around point. In the early season friendly, 
from short cover I witnessed Will Day's almost sinfully sensual leg 
glances. Best of all, not one but two instances of \emph{very nearly} 
run out sub by a man in jeans.

On my reading list for the winter is to go back to last year's ICEC 
report. It is important to keep issues in mind, to call out 
unacceptable behaviours if we should see them.

I have no remarkable queries recorded this year, though I enjoy the 
reprise of `retired hungover', and when the wicket-keeper is allowed to 
stray in front of the stumps. My DMs are open for entertaining 
discussion of any aspect which comes to mind.

If anyone would like to learn more about the electronic scoring I use, 
a matchday shadow is (almost) always welcome. This is not recruitment 
of an established colleague, but more resilience is not a bad thing. 

I will see you, if I am spared, for winter socials, and on that 
glorious day in spring with the season ahead of 
us\footnote{ie the maintenance day}.

\begin{centering}

 * * *
 
\end{centering}

I had a remark last year (but not for the first time) that what I had 
presented was rather too long for comfort. So I will keep this brief.

The stats speak for themselves. With a rather more successful 
background than last year I'd like to share, again, what I see that 
doesn't make the numbers. 

Spirit. The congratulating each other. The spotting that a teammate is 
having an off day and picking up for them, no hassle\footnote{I record 
here my gratitude to the Hague tour for carrying your scorer}. The 
cheering and encouragement on the field: to the ears of this Eeyorish 
character there is almost relentless positivity from some quarters (you 
know who you are). This is not recorded, but it's the spirit that makes 
the club, and I love you for it. 

Enough of looking back, I want to close looking forward. We know from 
club day that when we play with ourselves we lose, so can I thank in 
advance everyone who will give us a good run next season?


## Results
\begin{itemize}
	\item[1st] P16 W9 L7
	\item[2nd] P16 W12 L4
	\item[3rd] P15 W6 L9 
	\item[F] P6 W1 L5
	\item[Mid] P7 W4 L3
	\item[ALL] P60 W32 L28 
\end{itemize}

Not including the internal friendly or the Stoehr games.
(2023: played 66, won 20, lost 44, abandoned 2).

Seven games abandoned without a 
ball bowled, not including the abandoned spring tour (2023: 10; 2022: 
nil).


## Batting
Strike rates calculated using only innings in which balls faced are recorded. 

### Batting averages
Showing highest average first. 
Qualification: `r conf$qualify_inns_avgs` innings.

```{r bat-avgs-thisyear}
F.batavg.us.ty %>% D.batavg.bestbatavgs("Batting averages, this year")
```


### Most runs

Showing highest `r conf$default_list_length`.

```{r mostruns-thisyr}
F.batavg.us.ty %>%  D.batavg.mostruns("Most runs this year", conf$default_list_length)
```


### Fifties this year
```{r fifties-this-year}
a.numfifties <- nrow(F.batting.us.ty %>%
                       filter(Runs>=50))
```
There have been `r a.numfifties` fifties so far this season.
```{r fifties-this-year-2}
F.batting.us.ty %>% D.bat.fifties("Fifties this season")
```

### Fifties without a team win
Showing most recent `r conf$default_list_length`:
```{r fifties-no-win}
F.batting.us.ty %>% D.bat.fiftieslosing("Fifties without team win")
```

### Consecutive fifties

Showing consecutive fifties
```{r consecutive-batmilestones-ty}
F.batting.us.ty %>% D.bat.consecbatms("Consecutive fifties, this year", 50)
```

### Recent fifties, for each team
Showing most recent `r conf$default_list_length`:

```{r fifties-byteam, results='asis'}
 #cat( paste("#### ", names(conf$teams_of_interest)[i], " \n"))
map(conf$teams_of_interest, D.bat.batmsteam, cap=paste("Recent fifties"), 
    df=F.batting.us, ms=50)
```


### Top individual scores, by match type

Showing scores over 35,

```{r high-inns-type-ty, results='asis'}

map(levels(F.batting.us.ty$Type), D.bat.highestscorebytype , 
    cap= "Highest innings this year in",
    min=35,
    df=F.batting.us.ty )
```

### Primaries this season
```{r primaries}
F.batting.us.ty %>% D.bat.primaries("Primaries this season")
```


### Most ducks this season
```{r ducks}
F.batting.us.ty %>%  D.bat.duckcount("Ducks this season")
```

### Longest duck this season
```{r longduck}
F.batting.us.ty %>%  D.bat.ducklength("Long ducks this season")

```

### Sixes this season
```{r sixes-thisyear}
F.batavg.us.ty %>% D.batavg.sixcount("Most sixes this season")
```

### Carried bat
Position 1 or 2 and not out. Care! May not be accurate if retirements involved.

```{r carried-bat}
F.batting.us.ty %>% D.bat.carriedbat("Carried bat, this year")
```


## Partnerships

In the partnerships section, retirements are not handled cleanly. Retirements
are common in friendly games, any appearance here of a high partnership in a
friendly is likely to be spurious.

### Top scores for each wicket, this year

Showing the top few for each wicket, all club, where over 25
```{r top-pship-ty, results='asis'}
map(1:10, D.fow.pshiptopwkt, cap=paste("Our top scores this year"), df=F.fow.us.ty)
```


## Bowling

### Bowling averages
Qualification: `r conf$qualify_inns_avgs` innings.

```{r bowl-avgs-thisyear}
F.bowlavg.us.ty %>% D.bowlavg.best("Bowling averages, this season")
```

### Most wickets
Showing highest `r conf$default_list_length`.

```{r mostwkts-thisyear}
F.bowlavg.us.ty %>% D.bowlavg.wkt("Most wickets, this season", howmany=conf$default_list_length)
```

### Most wickets by match type
```{r mostwickts-ty-type, message=FALSE, warning=FALSE, results='asis'}
map(levels(F.bowling.us.ty$Type) , D.bowl.mostwktstype, cap="Most wickets",
    df = F.bowling.us.ty)
```



### Four-fors this year 
```{r fourfor-this-year}
a.numfourfors <- nrow(F.bowling.us.ty %>% filter(W>=4))
```
There have been `r a.numfourfors` four-fors so far this season.
```{r fourfor-this-year-2}
F.bowling.us.ty %>% D.bowl.fourfors("Four-fors this season")
```

### Consecutive four-fors

```{r consec-4for-ty}
F.bowling.us.ty %>% D.bowl.consecbowlms("Consecutive four-fors", 4)
```


### Dry days
```{r no-wickets}
F.bowling.us.ty %>% D.bowl.nowkts("No wickets, highest runs conceded")
```

### Outstanding analysis

In our matches and competitions

```{r strong-analysis-sph}
F.bowling.sphere.ty  %>%
  D.bowl.bestanalysis("Outstanding analysis, our competitions, this year")
```


### Gloves off

Bowling as designated wicketkeeper

```{r keeperbowl-ty}
F.allround.us.ty %>% D.allround.keeperbowling("Bowling this year as keeper")

```

\newpage

## Team

### Matches this year

```{r matches-ty}
F.matches.circle.ty %>% D.match.matchview("Our matches this year")
```

### Quotients

Overall,
```{r quotients}
D.inns.quotients(F.inningses.us.ty,F.inningses.them.ty, "Quotients")
```

By team, 
```{r quotients-byteam, results='asis'}
map(conf$teams_of_interest, D.inns.teamquotients, cap=paste("Quotients"), 
    df=F.inningses.circle.ty)
```

### Highest innings total
```{r high-inns-us-ty}
F.inningses.us.ty %>% D.inns.highinnstotal("Our highest innings totals, this season")
```

### Highest innings batting second
```{r high-inns-us-2-ty}
F.inningses.us.ty %>% D.inns.high2ndinns("Our highest innings totals 
                                         batting second, this season")
```

### Highest match aggregate
This section appears to contain spurious results.

```{r high-match-agg-circle}
F.matches.circle.ty %>% D.match.highmatchagg("Highest match aggregate, this season")
```

### Lowest innings total
```{r low-inns-us-ty}
F.inningses.us.ty %>% D.inns.lowinnstotal("Our lowest innings totals, this season")
```

### Most extras
```{r most-extras-us}
F.inningses.us.ty %>% D.inns.mostextras("Most extras in our innings")
```

### Tossing performance

```{r tossing-ty}
F.inningses.us.ty %>% D.inns.tossresult("Our tossing and match results this year")
```

\newpage

## All-rounder
### Thirty runs and three wickets in same match

```{r double-us-ty}
F.allround.us.ty %>% D.allround.matchdouble("Thirty and three-for", 30,3)

```


## Fielding

### Catches this year

Showing most first, including as wicket-keeper; most recent where tied.

```{r catches-thisyear}
F.fielding.us.ty %>% D.fielding.mostcatchesinns("Most catches in an innings, this year")


F.fieldsumm.us.ty %>% D.fieldsumm.mostcatches("Most total catches, this year", 
                                              howmany=conf$default_list_length)

```

### Victims per innings

Showing highest rate per innings, including as wicket-keeper. Qualification: four matches.

```{r victims-thisyear}
F.fieldsumm.us.ty %>% D.fieldsumm.mostdisperinns("Most dismissals per innings, this year")

```


## Wicket-keeping


### Dismissals this year, per innings

Showing most first; most recent where tied.

Excludes run-outs, because data are too flaky to be reliable.

```{r wkdiss-thisyear}
F.fielding.us.ty %>% D.fielding.mostblahinns( "Most WK catches in an innings, this year", "Ct")

F.fielding.us.ty %>% D.fielding.mostblahinns( "Most stumpings in an innings, this year", "Std")

F.fielding.us.ty %>% D.fielding.mostblahinns( "Most WK dismissals in an innings, this year", "Dis")

```

### Tally of dismissals, this year

Minimum: three.

```{r wkdiss-total-ty}
F.fielding.us.ty %>% D.fielding.mostblah("Most total WK catches, this year", "Ct")
F.fielding.us.ty %>% D.fielding.mostblah("Most total stumpings, this year", "Std")
F.fielding.us.ty %>% D.fielding.mostblah("Most total WK dismissals, this year", "Dis")

```

### No byes conceded for total of 150 or more
```{r no-byes-100-total-cy}
F.inningses.us.ty %>% D.inns.nobyes("No byes conceded for total of 150 runs or more, this season")

```


# Records: `r conf$club_name`

These are 'all-time' records. 'All time' means all of the dataset which is 
available, which may start after a player did.

## Batting
Strike rates calculated using only innings in which balls faced are recorded.

### Batting averages
Showing highest average first. 
Qualification: `r conf$qualify_inns_avgs` innings.

```{r bat-avgs-allt}
F.batavg.us %>% D.batavg.bestbatavgs("Batting averages, all time")
```

### Most runs

Showing highest `r conf$default_list_length`.

```{r mostruns-allt}
F.batavg.us %>%  D.batavg.mostruns("Career run totals", conf$default_list_length)
```

### Highest career strike rates
Minimum qualification: `r conf$qualify_balls_faced` balls faced
```{r bat-highSR-alltime}
F.batavg.us %>% D.batavg.highSR("Highest strike-rates, all time") 
```

### Most centuries
```{r centuries}
F.batavg.us %>% D.batavg.centurycount("Most centuries")
```

### Most ducks
```{r ducks-all, message=FALSE, warning=FALSE}
F.batting.us %>%  D.bat.duckcount("Count of ducks, all time")
```

### Longest duck
```{r longduck-all}
F.batting.us %>% D.bat.ducklength("Long ducks")
```

### Fifty on debut
'Debut' here means the first recorded innings in the dataset, which may have started
after a player's actual debut.
```{r fifty-debut}
F.batting.us %>% D.bat.batmsdebut("Fifties on debut")
```

### Centuries without a team win
Showing most recent `r conf$default_list_length`:
```{r cent-no-win-allt}
F.batting.us %>% D.bat.fiftieslosing("Centuries without team win", 100)
```

### Consecutive centuries

Showing consecutive centuries
```{r consecutive-batmilestones}

F.batting.us %>% D.bat.consecbatms("Consecutive centuries", 100)

```



### Top individual scores

```{r top-bat-performances}
F.batting.us %>% D.bat.highestscore("All-time highest scores")

```

### Top individual scores for each team
```{r topbat-byteam, results='asis'}
map(conf$teams_of_interest, D.bat.highestscorebyteam , 
    cap= "Highest innings for",
    min=35,
    df=F.batting.us)
```


### 200 runs before the end of May
```{r 200-end-May}
F.batting.us %>% D.bat.maybatms("200 runs in April and May")
```


### 500 runs in a season
```{r mostruns-season}
F.batting.us %>% D.bat.500season("500 runs in a season")
```

### Quickest to 500 in a season
Showing the date of match in which the 500th run was made
```{r quick500}
F.batting.us %>% D.bat.quickest500("Quickest to 500 in a season")
```

### Most fifties in a season
```{r mostfifties-season}
F.batting.us %>% D.bat.most50season("Most fifties in a season")
```

### Most boundaries in a season
```{r mostbounds-season}
F.batting.us %>% D.bat.mostbryseason("Most boundaries in a season")

```


### Monopolised batting
More than 60\% of the team's runs. Excludes scores of less than 10.

In March 1877, Charles Bannerman scored 165 from a team total of 245, 67.34\%.

```{r batting-monopoly}

F.batting.us %>% D.bat.bannerman("Monopolised runs", 0.6, 10)

```

### Batter outscoring the whole opposition

```{r outscore-opposition}
F.batting.us %>% D.bat.outscoringoppo("Outscoring the opposition")
```

### Most balls faced in an innings
```{r most-balls}
F.batting.us %>% D.bat.longinns("Longest innings")
```

### Most balls faced for a score 10 or less
```{r most-balls-lowscore}
F.batting.us %>% D.bat.longinns("Longest innings", 10)
```

### Most sixes in an innings
```{r most-sixes}
F.batting.us %>% D.bat.most6inns( "Most sixes in an innings")

F.batting.us %>% D.bat.mostBryinns("Most boundaries in an innings")
```

### Most career sixes
```{r career-sixes}
F.batavg.us %>% D.batavg.sixcount("Most career sixes")
```

### Most boundaries in an innings, for each team
```{r top4s-byteam, results='asis'}
map(conf$teams_of_interest, D.bat.mostBryinnsteam , 
    cap= "Most boundaries in an innings for",
    df=F.batting.us)
```


### Unusual dismissals
Out handled the ball, hit the ball twice, obstructing the field, timed out or hit wicket.

```{r unusual-dismissals}
F.batting.circle %>% D.bat.unusualdiss("Unusual dismissals, our matches")

#F.batting.sphere %>% D.unusualdiss("Unusual dismissals, our leagues")
```


\newpage
## Partnerships

In the partnerships section, retirements are not handled cleanly. Retirements
are common in friendly games, any appearance here of a high partnership in a
friendly is likely to be spurious.

### Top scores for each wicket, all time

Showing the top few for each wicket, all club,
```{r top-pship-alltime, results='asis'}
map(1:10, D.fow.pshiptopwkt, cap=paste("Our top scores"), df=F.fow.us)
```

### Big partnerships
```{r big-pship}
F.fow.us %>% D.fow.highpship("Partnerships over 150, all time", 150)

```

### Partnerships dominating the innings
```{r dompships}

F.fow.us %>% D.fow.dompship("Partnership over 80\\% of the total")

```


### Partnerships outscoring the whole opposition
```{r pshipsoveropp}

F.fow.us %>% D.fow.pshipoveropp("Partnership outscoring the opposition")

```

\newpage

## Bowling


### Bowling averages
Qualification: `r conf$qualify_inns_avgs` innings.

```{r bowl-avgs-alltime}
F.bowlavg.us %>% D.bowlavg.best("Bowling averages, all time")
```

### Most wickets
Showing highest `r conf$default_list_length`.

```{r mostwkts-alltime}
F.bowlavg.us %>% D.bowlavg.wkt("Most wickets, all time", conf$default_list_length)
```

### Most wickets by match type
```{r mostwickts-allt-type, message=FALSE, warning=FALSE, results='asis'}
map(levels(F.bowling.us$Type) , D.bowl.mostwktstype, cap="Most wickets",
    df = F.bowling.us)
```

### Most wickets in a season
```{r mostwkts-season}
F.bowling.us %>% D.bowl.mostwktseason("Most wickets in a season")
```

### Lowest average in a season
Qualification: bowled in `r conf$qualify_inns_avgs` innings.

```{r bestavg-season}
F.bowling.us %>% D.bowl.bestavgseason("Best average in a season") 
```

### Four-for on debut
'Debut' here means the first recorded bowling instance in the dataset, which may
have started
after a player's actual debut. Fielding without bowling is not considered as debut for
this table; it is debut with the ball.

```{r fourfor-debut}
F.bowling.us %>% D.bowl.msdebut("Four-for on debut")
```


### Consecutive five-fors

```{r consec-5for}
F.bowling.us %>% D.bowl.consecbowlms("Consecutive five-fors", 5)
```


### Dry days
```{r no-wickets-allt}
F.bowling.us %>% D.bowl.nowkts("No wickets, highest runs conceded")
```


### All maidens

Qualification: two or more

```{r all-maidens}
F.bowling.us %>% D.bowl.allmaidens("All maidens")
```

### Outstanding analysis
```{r strong-analysis-us}
F.bowling.us  %>%
  D.bowl.bestanalysis("Outstanding analysis, our club, all years")
```

### Cheapest five-for
```{r cheap-5for}
F.bowling.us %>% D.bowl.cheap5for("Cheapest five-fors, our club, all years") 
```

### Highest average with a five-for

```{r bowl-avgs-with-5for-at}
F.bowlavg.us %>% D.bowlavg.highavgwith5for("Highest career averages including
                                           a five-for, all time")

```

### Gloves off

Best analysis when bowling as designated wicketkeeper

```{r keeperbowl}
F.allround.us %>% D.allround.keeperbowling("Bowling as keeper")
```

### Quickest to 40 wickets

Showing the date on which they took their 40th wicket

```{r fastest40}
F.bowling.us %>% D.bowl.fast40("Fastest to 40 wickets in a season")
```


### Best career economy
Minimum qualification: `r conf$qualify_balls_bowled` balls bowled
```{r bowl-avgs-alltime-lowecon}
F.bowlavg.us %>% D.bowlavg.econ("Lowest economy, all time")
```

### Best career strike-rate
Minimum qualification: `r conf$qualify_balls_bowled` balls bowled
```{r bowl-avgs-alltime-bestsr}
F.bowlavg.us %>% D.bowlavg.sr("Best strike rate, all time")
```

### Most career five-fors
```{r bowl-avgs-alltime-most5}
F.bowlavg.us %>% D.bowlavg.most5wi("Most five-fors, all time")
```

### Five-fors without a team win
Showing most recent `r conf$default_list_length`:
```{r fourfor-no-win}
F.bowling.us %>% D.bowl.fiveforlose("Five-fors without team win")
```

\newpage

## Team

### Results
All teams, including friendlies and internal matches

```{r results}
A.resultssumm %>% D.resultsumm.results("Results by year")
```

### Highest innings totals

#### By us
```{r high-inns-us-allt}
F.inningses.us %>% D.inns.highinnstotal("Our highest innings totals, all time")
```

#### Against us
```{r high-inns-them-allt}
F.inningses.them %>% D.inns.highinnstotal("Our highest innings totals, all time")
```

#### Batting second
```{r high-inns-us-2-allt}
F.inningses.circle %>% D.inns.high2ndinns("Our highest innings totals batting second, all time")
```

### Highest innings totals losing one or no wickets
#### By us
```{r high-inns-us-for1}
F.inningses.us %>% D.inns.highforone("Highest innings by us for one or no wicket")
```

#### Against us
```{r high-inns-circle-for1}
F.inningses.them %>% D.inns.highforone("Highest innings against us for one or no wicket")
```

### High successful chases
In our matches
```{r high-chase}
F.inningses.circle %>% D.inns.highchase("Highest successful run chases")
```

### Lowest innings totals

Matches recorded as abandoned are excluded. Note that this also includes winning totals which reached 
an opponent's low total.

#### By us
```{r low-inns-us-allt}
F.inningses.us %>% D.inns.lowinnstotal("Our lowest innings totals, all time")
```

#### Against us
```{r low-inns-them-allt}
F.inningses.them %>% D.inns.lowinnstotal("Opponents' lowest innings totals, all time")
```

### Highest total without batting milestones
In all of our matches
```{r hightotal-nomilestone-us}
# TODO output a short scorecard here

F.inningses.circle %>% D.inns.hightotalnocent("Highest totals without any individual century", 100)

F.inningses.circle %>% D.inns.hightotalnocent("Highest totals without any individual fifty", 50)

```

### Multiple batting milestones 
```{r multiplebat-milestones}
# TODO output a short scorecard here

F.inningses.circle %>% D.inns.manycentury("Innings with two or more centuries")

F.inningses.circle %>% D.inns.manyfifty("Innings with three or more fifties")

```

### All batters contributing
Qualification: six or more batters in the innings, all into double figures

```{r allbats-doublefigs-us}
# TODO output a short scorecard here
F.inningses.circle %>% D.inns.allbatscontrib("Innings with all (6+) batters making 10 or more", 10, 6)
```


### Multiple bowling milestones 

Showing recent instances:

```{r multiplebowl-milestones}
# TODO output a short scorecard here

F.inningses.circle %>% D.inns.many4for("Innings with two four-fors",2)

F.inningses.circle %>% D.inns.allwkttakers("All bowlers taking at least two wickets")

```

### Conceding runs equitably

```{r equal-conceding-us}
# TODO output a short scorecard here
F.inningses.them %>% D.inns.equitbowl("Innings for 250+ with no bowler conceding 50", 250, 50)
```


### Ties
```{r ties-us}
F.matches.circle %>% D.match.ties("Tied matches")
```


### Most extras
This section appears to contain spurious results.

#### Our batting
```{r most-extras-us-alltime}
F.inningses.us %>% D.inns.mostextras("Most extras in our innings, all time")
```

#### Our bowling
```{r most-extras-them-alltime}
F.inningses.them %>% D.inns.mostextras("Most extras in our innings, all time")
```

### Highest match aggregate
This section appears to contain spurious results.

```{r high-match-agg-circle-allt}
F.matches.circle %>% D.match.highmatchagg("Highest match aggregate")
```

### Lowest match aggregate
This section appears to contain spurious results.

In completed matches:

```{r low-match-agg-allt}
F.matches.circle %>% D.match.lowmatchagg("Lowest match aggregate")
```


### Shortest completed matches
This section appears to contain spurious results, and does not account for 
eight-ball overs in evening games.

```{r short-complete}
F.matches.circle %>% D.match.short("Shortest completed matches")
```

### High winning margins

#### 250 runs or more
```{r highmarginruns}
F.inningses.circle %>% D.inns.winmargin("Wins by 250 runs or more", 1, 250, op=`>=`)
```

#### 10 wickets
```{r highmarginwkts}
F.inningses.circle %>% D.inns.winmargin("Wins by 10 wickets", 2, 10)
```

### Narrow winning margins

#### By 1 run
```{r lowmarginruns}
F.inningses.circle %>% D.inns.winmargin("Wins by 1 run or more", 1, 1, op=`==`)
```

#### By 1 wicket
```{r lowmarginwkt}
a.win1wktUs <- F.inningses.us %>% W.inns.winmargin(2, 1, op=`==`) %>% nrow()

a.win1wktThem <- F.inningses.them %>% W.inns.winmargin(2, 1, op=`==`) %>% nrow()
```

We have won `r a.win1wktUs` and lost `r a.win1wktThem ` matches by one wicket.

### Most runs for the club in a day
```{r daily-agg}
D.inns.dayagg(F.inningses.us, "Highest daily aggregate, this club")
```

### Tossing performance

```{r tossing-all}
F.inningses.us %>% D.inns.tossresult("Our tossing and match results, all time")
```
  
\newpage

## All-rounder

### Fifty runs and four wickets in same match

```{r little-double-us}
F.allround.us %>% D.allround.matchdouble("Fifty and four-for", 50,4)
```

### Hundred and five-for, our leagues

```{r double-sphere}
F.allround.sphere %>% D.allround.matchdouble("Hundred and five-for", 100, 5)
```

### Fifty runs and three fielding dismissals in same match

```{r fldr-double-us}
F.allround.us %>% D.allround.fielddouble("Fifty and three dismissals")
```

### Season double
500 runs and 20 wickets in a season

```{r season-double}
D.ar.seasondouble(F.batting.us, F.bowling.us, F.fielding.us, "Season double", 500, 20, 0)
```


500 runs and 10 dismissals

```{r season-fldg-double}
D.ar.seasondouble(F.batting.us, F.bowling.us, F.fielding.us, "Season double", 500, 0, 10)
```


### Career double
2000 runs and 50 wickets
```{r career-double-us}
# - allrounder := bat avg >= 15, <= 2.5 wkts/match
F.joinavgs.us %>% D.joinav.careerdouble("2000 runs and 50 wickets", 2000, 50, 0)
```

2000 runs and 50 fielding dismissals
```{r career-fldr-double-us}
F.joinavgs.us %>% D.joinav.careerdouble("2000 runs and 50 dismissals", 2000, 0, 50)
```

### Most appearances

```{r most-apps}

F.fielding.us %>% D.fielding.mostappsseason("Most appearances in a season")

F.fielding.us %>% D.fielding.appsalltime("Most appearances, all time")
```

\newpage

## Fielding

### Most catches in an innings

Showing most first, including as wicket-keeper; most recent where tied.

```{r catches-inns}
F.fielding.us %>% D.fielding.mostcatchesinns("Most catches in an innings, all-time")
```

### Tally of catches, all-time
Including as wicket-keeper. Showing highest `r conf$default_list_length`.

```{r catches-total}
F.fieldsumm.us %>% D.fieldsumm.mostcatches("Most total catches, all time", 
                                           conf$default_list_length)
```

### Most catches in a season
```{r mostcatch-season}
F.fielding.us %>% D.fielding.mostcatchseason("Most catches in a season")
```

\newpage

## Wicket-keeping

### Most dismissals in an innings

Showing most first; most recent where tied.

Excludes run-outs, because data are too flaky to be reliable.

```{r wkdiss-alltime}
F.fielding.us %>% D.fielding.mostblahinns( "Most WK catches in an innings, all time", "Ct")

F.fielding.us %>% D.fielding.mostblahinns( "Most stumpings in an innings, all time", "Std")

F.fielding.us %>% D.fielding.mostblahinns( "Most WK dismissals in an innings, all time", "Dis")

```

### Most dismissals in a season
```{r mostwkdis-season}
F.fielding.us %>% D.fielding.mostblahseason("Most WK catches in a season", "Ct")
F.fielding.us %>% D.fielding.mostblahseason("Most stumpings in a season", "Std")
F.fielding.us %>% D.fielding.mostblahseason("Most WK dismissals in a season", "Dis")
```

### Tally of dismissals, all time
Minimum: three.

```{r wkdiss-total}
F.fielding.us %>% D.fielding.mostblah("Most total WK catches, all time", "Ct")
F.fielding.us %>% D.fielding.mostblah("Most total stumpings, all time", "Std")
F.fielding.us %>% D.fielding.mostblah("Most total WK dismissals, all time", "Dis")

```

### Most appearances as wicket-keeper

```{r most-apps-wk}
F.fielding.us %>% D.fielding.mostappsseason("Most appearances in a season", "As keeper")

F.fielding.us %>% D.fielding.appsalltime("Most appearances, all time", "As keeper")
```


### No byes conceded for high totals
```{r no-byes-200-total}
F.inningses.them %>% D.inns.nobyes("No byes conceded for total of 150 runs or more, this season", ms=200)

```

\newpage

## Grounds

Considering only matches involving our club:

### Most total runs at a ground

```{r mostruns-ground}
F.inningses.circle %>% D.inns.groundmostruns("Most runs at grounds")
```

### Highest team score at a ground

```{r highteamtotal-ground}
F.inningses.circle %>% D.inns.groundhighteam("Highest team total at grounds")
```

### Highest individual score at a ground

```{r highindiviscore-ground}
F.batting.circle %>% D.bat.groundhighindiv("Highest individual score at grounds")
```

\newpage

# Tours

*By Will Day and The Tourists*

## MILTON at LEISURE, 2024

At Oxton, Cheshire, 13 April 2024. Abandoned before the toss.

At Milton, Notts, 14 April 2024. Abandoned before the toss.

\begin{verse}

When April with his frequent showers sweet\\
The drought of March has piercèd to the root,\\
And bathed each pitch, soft liquor soaking in\\
The turn, to bring the flowering of spin,\\
And joyful melody from crowds that cheer\\
While drinking all the day at ale and beer,\\
And stir in them desire for bat on ball,\\
Then cricketers make plans to go on tour,\\
And players seek to find bars of renown,\\
Play friendly clubs, based in distant towns.\\
And specially in twenty-four we'd wend,\\
Between the Dee and Mersey was our end,\\
A brisk and blissful friendly for to seek,\\
To strengthen that which winter's cloak made weak.\\
Our host at Childer lodgings for us bought,\\
At Aintree would they run at the King's sport,\\
At Oxted would we play a hundred ends,\\
And merry make with old and novel friends.\\
But all for nought, we bowlèd not a ball.\\
The winter rain, wild and greatest in all\\
The century left ground unfit for use.\\
Our consolation was: we did not lose.\\

\par\medskip

So we arranged we should watch others play,\\
In name alone was it a tailored day,\\
Ill fortune said a bus should take us tither:\\
We had no choice, it was no fault of Sivvers.\\
The Oval blessed in hazy morning sun\\
Saw Surrey back at forty-two for none.\\
Our lunch was liquid from St James' Gate\\
That Waitrose has at thirteen pounds for eight,\\
The pitch grew dry, the sun grew warm and we\\
Caught it in watching Sibley’s century.\\

\par\medskip

An artificial strip on Sunday fair \\
Saw sixteen come to warm up playing pairs.\\
A few good balls, a few good shots, the game\\
Was close: won by a run, and not by rain.\\
This tour's success was not in notches scored,\\
For cricket has the weather as its lord.\\
And better that we have our pitches rolled,\\
The less the chance we have of being bowled.\\

\end{verse}


## MILTON in THE HAGUE, 2024

*Happy in The Hague for a drunken hour*

Those on the ferry had an early start out of Milton for a 09.00 sailing
--  Race, Taylor, and While having already sampled the first of many 
outdoor café seating areas in what the signs described as `Historic 
Harwich'. The Eurostar contingent scarcely behind, but ahead on early 
beer stakes: Arun on the vanguard of the ferry beers, on his way to 
four. Will D fed his corporate machine, Sam explained the perfect 
chicken and sweetcorn wrap; others found, and presumably paid, the 
ferryman for a special visit to the car for the bat and duck costume 
needed for playing on a literal deck. We confused and delighted 
onlookers, losing only one ball to the waves. 

A change at Rotterdam brought the land-bound closer, meeting at the 
hostel: basic and fine, right on a square of several bars. We explored 
the options at a nearby food hall, Andy fixing the electrics in the 
corner to allow the first of many darts games. The number of players 
at their two-pint-peak meant quality of the gameplay matched that 
of the nasi goreng, though it was teetotal Sam who surprised us with a 
previously-unknown aptitude for the game, despite his difficulty in 
locating each number on the board. Our scorer notes only the result of 
the final game -- Nath won -- in a brewpub a short walk away. We ended 
the night back at the square, Pete demonstrating that sleeping is not 
just an indoor activity. 

Saturday saw us on the train to Amsterdam to watch the semi-final of 
the national 50-over competition with our hosts Voorburg against VRA 
Amsterdam. Leaving the department of silence and central Amsterdam's 
bizarre architecture, and with news of a delayed start, we strolled to 
a city park for lunch beside a rowing lake. So generous were 
the portions a croque-monsieur could be secreted, Paddington-style, for 
later. 

The delay was due to a wet pitch: even at this level, clumsiness in 
use of covers is still a thing. In a reduced 33-over game, Voorburg 
lost the toss and early wickets, making just 106. We chased shade on 
the balcony of the pavilion and later on the boundary. Soon after tea, 
Stock retired fucked, while others delighted in the biggest jugs you 
have ever seen: anything else, you'd have to go into town for. A 
delayed return still allowed time for hair washing, some quick 
unsheathed hoemoes, an Italian restaurant, a few half-litres in a 
London-styled dark pub, and bed.

Morning: tram to the beach and a stroll along the prom, which offered 
the full spectrum from tacky beach clubs blaring drum and bass, to empty 
chairs and weary cleaning staff, to high end beach volleyball 
facilities: or, a walk, under a cascade of bath pearls from giggling 
children, to gezellig café for coffee and excellent cake. Happy Toast 
promised but failed to deliver -- this as the sign of things to come.

Greeted at the ground by Kirk, our genial and welcoming Canadian/Kiwi 
host. We got underway briskly, winning the toss and batting. We weren't 
there to fellate mosquitos.

A meal after the game of biryani, little apple cakes, and beer. 
Voorburg gave us a lot of beer. And food. And more beer, and good chat. 
We had a lively discussion of London police and the price of milk (the 
ladies love it) in the taxi. Then just two more at Zeta, to 
Pete's long-anticipated credit, discussing Jos 
Buttler's average penis under the strongest fuck off home vibes this 
side of the \IJ. A club of sorts, Chlamydia Campari in charge as the 
stern guardian of the lav. A final late nightcap and some wordplay to 
close, one dorm room capturing Pete for what remained of the night.

Monday the most gentle of starts, a pancake breakfast and excellent 
supermarket cheese for a buffet lunch on the ferry. Only a few overs of 
ferry cricket were allowed, conditions being unfit through wind and 
sway. We dozed and discussed JSON, compiling ourselves into
readiness for the grey evening on the A14: bringing good Billy ashore
neither orange nor duck-yellow, but contented in seeing out the old
year in peaceful hope of more good times.

\medskip

The stats:

-  Sam Jones got four off nine,
-  43,9 km in four days, and one Day, walked,
-  ducks: many real, two metaphorical and one ersatz,
-  one tourist earning a gentle rebuke from the Dutch police.


### Voorburg CC ZaMi vs Milton CC

Only ODI.

At Voorburg, 8 September. Voorburg won by 4 wickets. Toss: Milton.


Thirteen off the first over showed promise but slowing a little, 
including Jay bowled just after his first run, and an early qualifier 
to wear the duck costume as Nath caught behind. Will C kept up the 
rate with lofty boundaries, hitting goalposts just beyond the rope, and 
retiring in the ninth over on fifty off 30 balls. 

Quick running of singles from 
Randy and Arun, the former bowled bringing Sam to continue the steady 
progress until caught at long on at the cusp of drinks, 88 for 4 off 
17. Arun caught behind shortly after, leaving Pete bringing form from 
the late season friendlies and Will D's sexy sweeps to put on 46 for 
the sixth wicket, ended with Pete bowled, and soon after Will hit only 
just low enough to be lbw. Phil giving the keeper his third catch, 
Niall narrowly avoiding the duck before chipping to gully, Chris making 
four tidy singles and caught at backward-point in the final over, 
giving 155 all out. 

Tea was pakoras and sheathed hummus, and just a 
little beer. The reply started well for Milton: 10 for 2 in the fifth 
over, one each for Dann and Jones, the latter an alert stumping from 
Day. The third came from Allen's first ball, drilled to A Sivajoti at 
square leg with the score at 19. 

That was to be the best of it: K Mirthi and M Qadar putting on 110 at 
around 7 an over. At drinks -- beer -- 101 for three after 16 could not 
inspire, a handful of good and tidy balls were not enough, though some 
honour was regained by three later catches: by N Sivajoti at cover off 
Dann, and two off Conlon, one by While at extra-cover and one 
behind.
Taylor bringing about the end in the 27th over, 
a missed half-chance then a high six from loose outside leg. 

\medskip


```{=latex}



\begin{tabularx}{0.82\textwidth}[t]{Xrrl}
\textbf{\large Milton}  & ~ & ~ & ~  \\
~       & ~ & \emph{B} & \emph{4/6} \\
W Conlon not out \dotfill & 60 & 35 &  7/2\\
J Dann b Krishna \dotfill & 1  & 15 & 0 \\
*N Sivajoti ct \dag{}Luciw b Krishna \dotfill & 0 & 1 & 0 \\
A Race b Koopman \dotfill & 15 & 19 &  1 \\
A Sivajoti ct \dag{}Luciw b Holleman \dotfill & 6  & 29 & 0 \\
S Jones ct Krishna b Batro \dotfill & 4  & 9 & 0 \\
\dag{}W Day lbw b de Graaf \dotfill & 17 & 37 &  1 \\
P While b Koopman \dotfill & 20 & 43 &  1 \\
P Allen ct \dag{}Luciw b Siro \dotfill & 0 & 5 & 0 \\
C Stock ct b Holleman \dotfill &  4 & 10 & 0 \\
N Taylor ct Kaushal b Holleman \dotfill & 1 & 8 & 0 \\
B 2, l-b 2, w 18, nb 5. \dotfill   & 27  &~&~\\ \cline{2-2}
~~~~~~~~~~~(all out, 34.3 ovs) & 155 &~&~\\ [2ex]
\end{tabularx}


\smallskip

1/34(2) 2/50(3) 3/79(4) 4/88(6) 5/88(5) 6/134(8) 7/135(9) 8/137(7) 9/140(11) 10/155(10)
Conlon retired at 50 (30b) when the score was 58/2 and Race 2*.
~

\smallskip

De Graaf 6-0-52-1, Krishna 4-1-11-2, Batro 5-0-22-1, Koopman 5-1-12-2, 
Holleman 3.3-0-13-3, Elsley 5-1-11-0, Koster 4-0-20-0, Siro 2-0-10-1.

\medskip 

\begin{tabularx}{0.82\textwidth}[t]{Xrrl}
\textbf{\large Voorburg}  & ~ & ~ & ~  \\
~       & ~ & \emph{B} & \emph{4/6} \\
Siro b Dann \dotfill & 1 & 7 & 0 \\
*\dag{}K Luciw std Day b Jones \dotfill & 4 & 9 & 0 \\
K Marthi retired not out \dotfill & 44 & 45 & 3/1 \\
M Koster ct A Sivajoti b Allen \dotfill & 2 & 7 & 0 \\
M Qadar retired not out \dotfill & 47 & 41 & 5/1 \\
P Krishna ct N Sivajoti b Dann \dotfill & 16 & 19 & 1 \\
J Batro ct While b Conlon \dotfill & 5 & 8 & 0 \\
Dave ct \dag{}Day b Conlon \dotfill & 4 & 10 & 0 \\
S de Graaf not out \dotfill & 16 & 10 & 0/2 \\
Nick not out \dotfill & 1 & 1 & 0 \\
B 2, w 13, nb 2 \dotfill   & 17  &~&~\\ \cline{2-2}
~~~~~~~~~~~(6 wkts, 26.3 ovs) & 157 &~&~\\ [2ex]
\end{tabularx}

\smallskip

1/1(1) 2/10(2) 3/18(4) 4/128(6) 5/133(7) 6/145(8). 
Marathi retired at 100/4 (Qadar 36*) and Qadar retired at 134/6 (Dave 0*)

\smallskip

F Holleman did not bat.

\smallskip

Jones 4-0-11-1, Dann 6-0-24-2, Race 2-0-13-0, Allen 2-0-22-1, 
Stock 2-0-19-0, N Sivajoti 2-0-10-0, While 2-0-15-0, 
A Sivajoti 2-0-19-0, Conlon 4-0-16-2, Taylor 0.3-0-6-0.

```

\newpage

# Stoehr Memorial Tournament, 2024



## A third year for the Stoehr games brings new success

<!-- *By Ed Conlon* -->

The third Peter Stoehr memorial game  on 30 June 
brought club members, families, 
and friends to play and watch a day of relaxed and joyfully 
competitive cricket.

Since losing Peter in 2020 the club has held fundraising days in 
his memory. 
This year we repeated the six-a-side format from 2023, this time
with six teams. Each side batted for five overs, and everyone
except the keeper bowls. 

Although four teams were invited `external' sides, there was strong
Milton representation across the slate. And surely for such an 
occasion we would put our individual pride to one side, and let
cricket be the winner, wouldn't we?

Almost. 

The first innings had the President's team hit a loosely Press 
\& Assessment based team for 80, the highest total of the day; missing
their star batter from last year Julius Jackson, CUPA would later 
fall well short in the chase.

Things settled down then -- the barbeque was lit, the bar open, and
Milton players old and new shared out nice shots and good balls. 

We kept the games pacy and with many small sides, there was plenty
of time to sit and watch with a burger, drink and snacks from the 
wide selection on offer, donated by club members.

Top individual score of the day, 46 not out from Nick Widdowson, aided
no doubt by Ollie taking any remaining shine off the ball early, was
only just enough to hold off Blobble's Wobbles, who Will Jupp had
coaxed down from London for the day with the promise of good cake. 
They would be kind enough to come back a few months later, even after 
we'd made them face the rather tidy Waterbeach bowling.

Our friends from Reach were also there for a day out, losing only
one wicket across both their group games and winning both.

We paused for the raffle and some well-chosen words. It was a delight
to see so many had come to the event: families in particular, 
showing that we are part of a bigger community with the open and welcoming
spirit of Milton CC in full swing. 

Back to the cricket, our own Milton side also won both their group 
games but in a baffling, stats-driven format point, they played off 
with Reach progressing to see Blobble's Wobbles again, sent into the 
final by rep\^{e}chage. Reach won, we shall say easily,  in good time.

Although the cricket wrapped up earlier than last year as England were 
playing another sport that evening, many stayed around in the 
clubhouse to help with the leftovers and keep the donations going. 

This event is becoming a highlight of the season for many and 
was again a special day in memory of Peter. This year we
raised a record \pounds1200, with a donation being made to the Air Ambulance 
charity and, through the generosity of the Stoehr family, 
retained in the club.

Milton CC would again like to extend a huge thanks to all who 
attended, played and helped make it happen. See you next time.

## Teams

### CUPA
  Phil Allen\dag{},
  Will Day*,
  Chris Goodall,
  Sam Jones, 
  Chris Stock,
  Pete While.

### President's VI
 Mark Barton*,
 Ed Conlon,
 Ani Ghosh,
 Jez Major,
 Zack Smith\dag{},
 Adam South.

### Waterbeach
 Ed Cree,
 Pradeep Gowda\dag{},
 Rakesh Panigrahi*,
 Andy Peck,
Alastair, 
Temoc.

### Milton
 Noah Barton,
 Jay Dann,
 Nathan Sivajoti*\dag{},
 Nick Widdowson,
Ollie, 
Tarquin.

### Reach
 M Mead*,
 Ewan Cameron,
 T Clark,
 Ross Clark,
 Tony Fordham,
 Archie Fordham,
 James Henderson\dag{}.

### Blobble's Wobbles
Mr H Boutflower,
Mr J Goodhart,
Mr J Jones,
Jupp,
Mr W Mathewson,
Mr R Uloth*\dag{}.

## Results

All played at The Sycamores, 30 June 2024. Conditions: fair, warm, jovial.

1.  President's VI bt CUPA by 41 runs
2.  Reach bt President's VI by 13 runs
3.  Blobble's Wobbles bt Waterbeach by 16 runs
4.  Reach bt CUPA by 5 wickets
5.  Milton bt Blobble's Wobbles by 7 runs
6.  Milton bt Waterbeach by 3 wickets

\medskip

Reach and Milton progress to semi-final. In the semi-final, Reach (38/1, 4.5 ovs)
beat
Milton (37/3, 5 ovs) by four wickets.

\bigskip

Blobble's Wobbles move to the final by having the highest net quotient
from among those not in the semi-final.

\bigskip

Final: Reach (46/0, 2.2 ovs) beat Blobble's Wobbles (45/0, 5 ovs) by
5 wickets.

\bigskip


## Batting
```{=latex}
\setlength{\tabcolsep}{2pt}
\begin{tabularx}{0.95\textwidth}[h]{X*{7}{r}ll}
\textbf{Name} & \textbf{M} & \textbf{I} & \textbf{NO} & 
  \textbf{Runs} & \textbf{HS} & \textbf{Avg} & \textbf{SR}
  & \textbf{4/6} & \textbf{Ct}\\ \hline \hline

%Julius Jackson &  3 & 2 & 2 & 62 & 42* & - & 482.35 & 1/8 & 1\\

M Mead      	&4&	3&	3&	96&	34*&	--&	259.45&	5/8	    &~      \\
N Widdowson	    &3&	3&	3&	59&	46*&	--&	268.18&	11/1	&1          \\
S Jones	        &4&	3&	2&	47&	28& 	47&	180.76&	4/3	    &~     \\
E Conlon	    &2&	2&	1&	42&	25*&	42&	182.60&	4/2	    &~    \\
R Uloth	        &3&	3&	1&	38&	25*&	19&	135.71&	5	    &~      \\
E Cameron	    &4&	3&	2&	37&	20&	    37&	176.19&	2/2	    &~      \\
H Boutflower	&3&	3&	2&	34&	19*&	34&	154.54&	3	    &~     \\
J Major	        &3&	2&	2&	32&	19&	    --&	177.77&	5	    &~      \\
W Jupp	        &3&	2&	1&	29&	18&	    29&	193.33&	5	    &~      \\
A Ghosh     	&2&	1&	1&	24&	24*&	--&	342.85&	3/1	    &~      \\
J Dann	        &4&	3&	0&	24&	14&	     8&	114.28&	2	    &~      \\
P Gowda	        &2&	2&	1&	16&	9*&	    16&	228.57&	3	    &~      \\
Alastair	    &1&	1&	1&	16&	16*&	--&	114.28&	1	    &~      \\
W Day	        &2&	1&	0&	16&	16&	    16&	145.45&	3	    &~      \\
J Henderson  	&3&	2&	1&	16&	10&	    16&	177.77&	4/1	    &~      \\
P Allen	        &2&	2&	2&	15&	14*&	--&	93.75&	2	    &~      \\
A Fordham	    &4&	1&	1&	14&	14*&	--&	107.69&	1	    &~      \\
T Fordham	    &4&	1&	1&	13&	13*&	--&	118.18&	2	    &~      \\
A Peck       	&2&	2&	0&	13&	10&	    6.5&	81.25&	1	&~          \\
J Jones	        &3&	1&	1&	10&	10*&	--&	250.00&	1	    &~      \\
Z Smith      	&2&	2&	0&	9&	8&	    4.5&	128.57&	1	&~          \\
N Sivajoti	    &2&	1&	1&	7&	7*&	    --&	87.50&	~&	1          \\
N Barton	    &3&	2&	1&	7&	5&	     7&	35.00&	~&	          \\
W Mathewson	    &3&	2&	1&	5&	4*&	    5&	62.50&	~&	          \\
P While	        &1&	1&	0&	4&	4&	    4&	66.66&	~&	1          \\
J Goodhart	    &3&	2&	0&	4&	4&	    2&	44.44&	~&	          \\
C Stock      	&2&	1&	1&	3&	3*&	    --&	37.50&	~&	          \\
Temoc	        &2&	1&	0&	1&	1&	     1&	33.33&	~&	1          \\
M Barton	    &3&	1&	0&	1&	1&	     1&	33.33&	~&	          \\
E Cree	        &2&	2&	1&	1&	1&	     1&	20.00&	~&	          \\

Ollie	        &2&	2&	0&	0&	0&    	0	&0.00&	~&	1          \\
R Clark	        &2&	0&	0&	0&	--&	    --&	--	&	~&1          \\
R Panigrahi	    &2&	0&	0&	0&	--&	    --&	--	&	~&1          \\


A South	        &3&	1&	0&	0&	0&	     0&	0.00&	~&	          \\
C Goodall	    &2&	1&	0&	0&	0&	     0&	0.00&	~&	          \\

T Clark	        &1&	0&	0&	0&	--&	    --&	--	&	~&          \\
Tarquin	        &3&	0&	0&	0&	--&	    --&	--	&	~&          \\

\end{tabularx}

```
\newpage

## Bowling
```{=latex}


\begin{tabularx}{0.95\textwidth}[h]{Xl*{7}{r}}
\textbf{Name} & \textbf{B} & \textbf{D} & \textbf{R} & 
  \textbf{W} & \textbf{SR} & \textbf{Avg} & \textbf{Econ}\\ \hline \hline
Widdowson&	18&	9&	18&	3&	6.00&	6.00&	6.00\\
Jones	S&	18&	7&	24&	3&	6.00&	8.00&	8.00\\
Fordham A &	24&	13&	21&	2&	12.00&	10.50&	5.25\\
Panigrahi&	12&	5&	21&	2&	6.00&	10.50&	10.50\\
Fordham T&	24&	4&	47&	2&	12.00&	23.50&	11.75\\
Jupp	&	6&	4&	2&	1&	6.00&	2.00&	2.00\\
Alastair&	3&	1&	6&	1&	3.00&	6.00&	12.00\\
Peck	&	12&	8&	9&	1&	12.00&	9.00&	4.50\\
Barton M&	6&	1&	9&	1&	6.00&	9.00&	9.00\\
Uloth	&	8&	4&	12&	1&	8.00&	12.00&	9.00\\
Barton N&	17&	6&	15&	1&	17.00&	15.00&	5.29\\
Stock	&	12&	3&	16&	1&	12.00&	16.00&	8.00\\
Cree	&	12&	4&	20&	1&	12.00&	20.00&	10.00\\
Ghosh	&	12&	2&	25&	1&	12.00&	25.00&	12.50\\
Major	&	18&	8&	30&	1&	18.00&	30.00&	10.00\\
Mead	&	24&	7&	32&	1&	24.00&	32.00&	8.00\\
Temoc	&	18&	6&	37&	1&	18.00&	37.00&	12.33\\
Clark	R&	12&	7&	8&	0&	--&	--&	4.00\\
Clark	T&	6&	1&	9&	0&	--&	--&	9.00\\
Gowda	&	6&	3&	12&	0&	--&	--&	12.00\\
Barton	&	12&	2&	15&	0&	--&	--&	7.50\\
South	&	12&	5&	17&	0&	--&	--&	8.50\\
While	&	6&	1&	18&	0&	--&	--&	18.00\\
Conlon	&	12&	4&	19&	0&	--&	--&	9.50\\
Dann	&	12&	4&	19&	0&	--&	--&	9.50\\
Ollie	&	12&	1&	23&	0&	--&	--&	11.50\\
Goodall	&	7&	0&	23&	0&	--&	--&	19.71\\
Boutflower&	12&	1&	26&	0&	--&	--&	13.00\\
Cameron	&	18&	4&	27&	0&	--&	--&	9.00\\
Goodhart&	12&	1&	28&	0&	--&	--&	14.00\\
Jones J	&	18&	9&	30&	0&	--&	--&	10.00\\
Tarquin	&	18&	5&	32&	0&	--&	--&	10.66\\
Mathewson&	18&	3&	38&	0&	--&	--&	12.66\\
Day		&	12&	0&	42&	0&	--&	--&	21.00\\


\end{tabularx}


```
\newpage
## Scorecards
```{=latex}

Editor's note: in this section, bowling figures are given as
balls-dots-runs-wickets.



\newlength{\oldtabcolsep}
\setlength{\oldtabcolsep}{\tabcolsep}
\setlength{\tabcolsep}{2pt}

```

### President's VI vs CUPA
```{=latex}
President's VI win by 41 runs.

\medskip

\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright
\textbf{President's VI}
\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
%\textbf{\large President's VI}  & ~ & ~ & ~  \\
~       & ~ & \emph{B} & \emph{4/6} \\
1 \dag{}Z. Smith     \emph{b 3}     \dotfill & 8   & 4  & 1 \\
2 J. Major           \emph{not out} \dotfill & 19  & 7  & 4 \\
3 E. Conlon          \emph{c 7 b 6} \dotfill & 17  & 8  & 2/1 \\
4 A. Ghosh           \emph{not out} \dotfill & 24  & 7  & 3/1 \\
B 1, lb 1, w 8, nb 2    & 12  &~&~\\ \cline{2-2}
~~~(2 wkts, 5 ovs) & 80 &~&~\\ [2ex]

\end{tabularx}

\smallskip

1/10(1) 2/39(3)

\smallskip

5 A. South and  6 *M. Barton did not bat. 

\smallskip

Jones 6-1-11-1, While 6-1-18-0, Stock 6-2-8-1, Goodall 6-0-18-0, 
Day 6-0-23-0.

\end{minipage}%
%\hfill
\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright
\textbf{CUPA}

\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
~       & ~ & \emph{B} & \emph{4/6} \\
1 \dag{}P. Allen    \emph{not out} \dotfill & 14  &  15 & 2 \\
2 J. Dann           \emph{b 4}     \dotfill & 8   &  10 & - \\
3 S. Jones          \emph{not out} \dotfill & 13  &  4  & 1/1 \\
W 2, nb 2   & 4  &~&~\\\cline{2-2}
~~~(1 wkt, 5 ovs) & 39 &~&~\\ [2ex]

\end{tabularx}

\smallskip

1/25(2)

\smallskip

4. *W. Day, 5 C. Goodall and 6 C. Stock did not bat. 7. P While fielded.

\smallskip

Major 6-3-9-0, South 6-4-3-0, Conlon 6-1-8-0, Barton 6-2-5-0, 
Ghosh 6-1-14-1.
\end{minipage}



```

### Reach vs President's VI
```{=latex}
Reach win by 13 runs.

\medskip

\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright

\textbf{ Reach } 
\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
~       & ~ & \emph{B} & \emph{4/6} \\
1 *M. Mead             \emph{not out} \dotfill & 29   & 15  & 1/2 \\
2 E. Cameron           \emph{b 3}     \dotfill & 20  & 11  & 2/1 \\
3 \dag{}J. Henderson   \emph{not out} \dotfill & 6  & 4  & 2/1 \\
B 3, lb 2   & 5  &~&~\\ \cline{2-2}
~~~(1 wkt, 5 ovs) & 60 &~&~\\ [2ex]

\end{tabularx}

\smallskip

1/49(2).

\smallskip

4 T. Fordham, 5 A. Fordham and 6 T. Clark did not bat. 

\smallskip

Ghosh 6-1-11-0, South 6-1-14-0, Conlon 6-3-11-0, Major 6-3-9-1,
Barton 6-0-10-0.

\end{minipage}%
\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright
\textbf{ President's VI} 
\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
~       & ~ & \emph{B} & \emph{4/6} \\
1 \dag{}Z. Smith     \emph{c\&{}b 5} \dotfill & 1    &  3  & - \\
2 E. Conlon          \emph{not out}  \dotfill & 25   &  15 & 2/1 \\
3 J. Major           \emph{not out}  \dotfill & 13   &  11 & 1 \\
W 2, nb 6   & 8  &~&~\\\cline{2-2}
~~~(1 wkt, 5 ovs) & 47 &~&~\\ [2ex]

\end{tabularx}

\smallskip

1/2(1)

\smallskip

4 *M. Barton, 5 A. South and 6 A. Ghosh did not bat.

\smallskip

A Fordham 6-4-2-1, Mead 6-1-9-0, Clark 6-1-9-0, Cameron 6-1-11-0,
T Fordham 6-1-16-0.

\end{minipage}
```


### Blobble's Wobbles vs Waterbeach
```{=latex}
Blobble's Wobbles win by 16 runs.

\medskip

\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright

\textbf{ Blobble's Wobbles } 
\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
~       & ~ & \emph{B} & \emph{4/6} \\
1 H. Boutflower        \emph{b 7} \dotfill & 10   & 5  & 2 \\
2 *\dag{}R. Uloth       \emph{b 1}     \dotfill & 6  & 7  & 1 \\
3 W. Mathewson          \emph{c 2 b 3} \dotfill & 1  & 3  & - \\
4 J Goodhart            \emph{b 6} \dotfill & 0  & 3  & - \\
5 W. Jupp               \emph{not out} \dotfill & 11  & 7  & 2 \\
6 J. Jones              \emph{not out} \dotfill & 10  & 4  & 1 \\
B 1, w 2, nb 10   & 13  &~&~\\ \cline{2-2}
~~~(4 wkts, 5 ovs) & 51 &~&~\\ [2ex]

\end{tabularx}

\smallskip

1/16(1) 2/18(3) 3/24(2) 4/39(4).

\smallskip

~

\smallskip

Temoc 6-2-16-1, Cree 6-3-3-1, Peck 6-4-7-1, Gowda 6-3-12-0, 
Panigrahi 6-2-12-1.

\end{minipage}%
\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright
\textbf{ Waterbeach} 
\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
~       & ~ & \emph{B} & \emph{4/6} \\
1 A. Peck    \emph{lbw b 5} \dotfill & 10    &  10  & 1 \\
2 \dag{}P. While    \emph{r 5}  \dotfill & 4   &  6 & - \\
3 E. Cree           \emph{run out}  \dotfill & 0   &  3 & - \\
4 P. Gowda          \emph{not out}  \dotfill & 9   &  4 & 2 \\
5 A. South          \emph{run out}  \dotfill & 0   &  3 & - \\
B 2, w 8, nb 2   & 12  &~&~\\\cline{2-2}
~~~(4 wkts, 5 ovs) & 35 &~&~\\ [2ex]

\end{tabularx}

\smallskip

1/16(2) 2/16(1) 3/20(3) 4/35(4).

\smallskip

6 *R. Panigrahi did not bat. 7 Temoc fielded.

\smallskip

Boutflower 6-1-10-0, Mathewson 6-2-4-0, Jupp 6-4-2-1, 
Jones 6-5-4-0, Goodhart 6-1-13-0.

\end{minipage}

```

### CUPA vs Reach
```{=latex}
Reach win by 5 wickets.

\medskip

\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright
\textbf{CUPA } 
\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
~       & ~ & \emph{B} & \emph{4/6} \\
1 S. Jones       \emph{c 3 b 1} \dotfill & 6   & 6  & 1 \\
2 *W. Day       \emph{b 4}     \dotfill & 16  & 11  & 3 \\
3 C. Stock          \emph{not out} \dotfill & 3  & 8  & - \\
4 C. Goodall            \emph{b 4} \dotfill & 0  & 1  & - \\
5 \dag{}P. Allen               \emph{not out} \dotfill & 1 & 1  & - \\
B 6, w 7, nb 4   & 17  &~&~\\ \cline{2-2}
~~~(3 wkts, 5 ovs) & 43 &~&~\\ [2ex]

\end{tabularx}

\smallskip

1/17(1) 2/41(2) 3/41(3).

\smallskip

6 J. Dann did not bat.

\smallskip

A Fordham 6-3-7-0, Mead 6-2-8-1, Tarquin 6-1-14-0, Clark 6-3-4-0, T Fordham 6-3-4-2.

\end{minipage}%
\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright
\textbf{Reach} 
\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
~       & ~ & \emph{B} & \emph{4/6} \\
1 *\dag{}M. Mead    \emph{not out} \dotfill & 33    &  13  & 2/2 \\
2 E. Cameron    \emph{not out}  \dotfill & 7   &  5 & - \\
B 2, l-b 1, w 4   & 7  &~&~\\\cline{2-2}
~~~(no wkts, 3.1 ovs) & 47 &~&~\\ [2ex]

\end{tabularx}

\smallskip

~

\smallskip
3 R. Clark, 4 T. Fordham, 5 A. Fordham, 6 Tarquin did not bat.

%Fuck knows who bowled or did not bat, the scoresheet is a mess, thanks guys

\smallskip

Day 6-0-19-0, Dann 6-1-13-0, Stock 6-1-8-0, Goodall 1-0-4-0.

\end{minipage}
```

### Milton vs Blobble's Wobbles
```{=latex}
Milton win by 7 runs.

\medskip

\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright
\textbf{Milton } 
\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
~       & ~ & \emph{B} & \emph{4/6} \\
1 Ollie        \emph{b 3} \dotfill & 0   & 3  & - \\
2 *\dag{}N. Sivajoti       \emph{not out}     \dotfill & 7  & 8  & - \\
3 N. Widdowson    \emph{not out} \dotfill & 46  & 18  & 8/1 \\

L-b 2, w 2, nb 2   & 6  &~&~\\ \cline{2-2}
~~~(1 wkt, 5 ovs) & 59 &~&~\\ [2ex]

\end{tabularx}

\smallskip

1/0(1).

\smallskip

4 S Jones, 5 Temoc, and 6 N Barton did not bat.

\smallskip

Uloth 6-4-5-1, Goodhart 6-0-15-0, Jones 6-3-6-0, 
Mathewson 6-1-15-0, Boutflower 6-0-16-0.

\end{minipage}%
\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright
\textbf{ Blobble's Wobbles} 
\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
~       & ~ & \emph{B} & \emph{4/6} \\
1 J. Goodhart    \emph{c\&b 3} \dotfill & 4    &  6  & - \\
2 \dag{}W. Jupp    \emph{b 3}  \dotfill & 18   &  8 & 3 \\
3 *R. Uloth           \emph{c 1 b 4}  \dotfill & 7   &  4 & 1 \\
4 W. Mathewson          \emph{not out}  \dotfill & 4   &  5 & - \\
5 H. Boutflower          \emph{not out}  \dotfill & 5   &  4 & - \\
B 1, l-b 1, w 6, nb 6   & 14  &~&~\\\cline{2-2}
~~~(3 wkts, 5 ovs) & 52 &~&~\\ [2ex]

\end{tabularx}

\smallskip

1/33(2) 2/36(1) 3/40(3).

\smallskip

6 J. Jones did not bat. 

\smallskip

Ollie 6-1-11-0, Temoc 6-0-17-0, Widdowson 6-2-7-2, Jones 6-4-8-1,
Barton 6-1-7-0.

\end{minipage}
```


### Waterbeach vs Milton
```{=latex}
Milton win by 3 wickets.

\medskip

\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright
\textbf{ Waterbeach } 
\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
~       & ~ & \emph{B} & \emph{4/6} \\
1 Alastair        \emph{not out} \dotfill & 16  & 14  & 1 \\
2 \dag{}P. Gowda       \emph{b 5}     \dotfill & 7  & 3  & 1 \\
3 A. Peck        \emph{c 6 b 1} \dotfill & 3  & 6  & - \\
4 Temoc            \emph{b 3} \dotfill & 1  & 3  & - \\
5 E. Cree               \emph{not out} \dotfill & 1  & 2  & - \\
B 2, w 4, nb 2   & 8  &~&~\\ \cline{2-2}
~~~(3 wkts, 5 ovs) & 36 &~&~\\ [2ex]

\end{tabularx}

\smallskip

1/16(2) 2/25(3) 3/31(4).

\smallskip

6 *R. Panigrahi did not bat

\smallskip

Ollie 6-0-12-0, Widdowson 6-4-6-1, Jones 6-2-5-1, Dann 6-3-6-0,
Barton 6-3-5-1.

\end{minipage}%
\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright
\textbf{Milton}
\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
~       & ~ & \emph{B} & \emph{4/6} \\
1 S. Jones    \emph{retired} \dotfill & 28    &  16  & 2/2 \\
2 J. Dann    \emph{c\&b 6}  \dotfill & 2   &  2 & - \\
3 N. Barton           \emph{not out}  \dotfill & 2   &  6 & - \\
4 Ollie         \emph{c 4  b 1}  \dotfill & 0   &  2 & - \\
5 N. Widdowson          \emph{not out}  \dotfill & 4   & 1 & 1 \\
Nb 2   & 2  &~&~\\\cline{2-2}
~~~(2 wkts, 4.3 ovs) & 38 &~&~\\ [2ex]

\end{tabularx}

\smallskip

1/26(2) 2/34(4). Jones retired at 32/1.

\smallskip

6 *\dag{}N. Sivajoti did not bat. 

\smallskip

Cree 6-1-17-0, Panigrahi 6-3-9-1, Peck 6-4-2-0, 
Temoc 6-4-4-0. Alastair 3-1-6-1.

\end{minipage}

```

### Quotients
```{=latex}

\begin{tabularx}{0.95\textwidth}[t]{X*{7}{r}}
~ & \multicolumn{2}{ c }{Runs} & \multicolumn{2}{ c }{Wkts} & \multicolumn{3}{ c }{Quotient} \\
Team & F &  A & A & F & F & A & Net \\ \hline \hline
Reach & 107 & 90 & 1 & 4 & 107.00 & 22.50 & 84.50 \\
Milton & 97 & 88 & 2 & 6 & 48.50 & 14.66 & 33.83 \\

Blobble's Wobbles & 103 & 94 & 7 & 5 & 14.71 & 18.80 & -4.08 \\
President's VI & 127 & 99 & 3 & 2 & 42.33 & 49.50 & -7.16 \\

Waterbeach & 71 & 89 & 7 & 5 & 10.14 & 17.80 & -7.65 \\
CUPA & 82 & 127 & 4 & 2 & 20.50 & 63.50 & -43.00 \\ 

\end{tabularx}


```

### Semi-final: Milton vs Reach
```{=latex}
Reach win by 4 wickets.

\medskip

\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright
\textbf{Milton} 
\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
~       & ~ & \emph{B} & \emph{4/6} \\
1 *M. Barton  \emph{b 3} \dotfill & 1  & 3  & - \\
2 N. Barton  \emph{r 1} \dotfill & 5  & 14  & - \\
3 \dag{}J. Dann \emph{run out} \dotfill & 14  & 9  & 2 \\
4 N. Widdowson \emph{not out} \dotfill &  9 & 3  & 2 \\
W 2, nb 6    & 8  &~&~\\ \cline{2-2}
~~~(3 wkts, 5 ovs) & 37 &~&~\\ [2ex]

\end{tabularx}

\smallskip

1/4(1) 2/27(2) 3/37(3).

\smallskip

5 J. Major, 6 Tarquin did not bat.

\smallskip

A Fordham 6-2-7-1, Mead 6-2-7-0, R Clark 6-4-4-0, Cameron 6-2-7-0,
T Fordham 6-0-12-0.

\end{minipage}%
\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright
\textbf{Reach} 
\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
~       & ~ & \emph{B} & \emph{4/6} \\
1 T. Fordham  \emph{not out} \dotfill & 13  &  11 & 2 \\
2 \dag{}J. Henderson \emph{lbw b 1} \dotfill &  10 &  5 & 2 \\
3 A. Fordham \emph{not out} \dotfill & 14  & 13  & 1 \\
L-b 1   & 1  &~&~\\\cline{2-2}
~~~(1 wkt, 4.5 ovs) & 38 &~&~\\ [2ex]

\end{tabularx}

\smallskip

1/21(2).

\smallskip
 4. *M Mead, 5 R. Clark and 6 E. Cameron did not bat.

\smallskip

Major 6-2-10-0, Tarquin 6-2-11-0, M Barton 6-1-9-1, Widdowson 6-3-5-0,
N Barton 5-2-3-0.

\end{minipage}
```


### Final: Blobble's Wobbles vs Reach 

```{=latex}
Reach win by 5 wickets. Toss: Blobble's Wobbles.

\medskip

\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright

\textbf{Blobble's Wobbles}
\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
~       & ~ & \emph{B} & \emph{4/6} \\
1. H. Boutflower   not out  \dotfill & 19  & 13  & 1 \\
2. *\dag{}R. Uloth  not out \dotfill & 25  & 17  & 3 \\
L-b 1 \dotfill   & 1  &~&~\\ \cline{2-2}
~~~(no wkts, 5 overs) & 45 &~&~\\ [2ex]
\end{tabularx}

\smallskip

3. W. Mathewson, 4. J Goodhart, 5. W Jupp and 6. J Jones did not bat.

\smallskip

A Fordham 6-4-5-0, Mead 6-2-8-0, Tarquin 6-2-7-0,
Cameron 6-1-9-0, T Fordham 6-0-15-0.

\end{minipage}%
\noindent
\begin{minipage}[t]{.5\textwidth}
\raggedright

\textbf{Reach} 
\begin{tabularx}{0.95\textwidth}[t]{Xrrl}
~       & ~ & \emph{B} & \emph{4/6} \\
1. *M. Mead not out \dotfill & 34  & 9  & 2/4 \\
2. E. Cameron not out \dotfill & 10  & 5  & 0/1 \\

B 2 \dotfill   & 2  &~&~\\ \cline{2-2}
~~~(no wkts, 2.2 overs) & 46 &~&~\\ [2ex]
\end{tabularx}

\smallskip

3. T. Fordham, 4. Tarquin, 5. A. Fordham and 6. \dag{}J. Henderson did not bat.

\smallskip

Jones 6-1-20-0, Mathewson 6-0-19-0, Uloth 2-0-7-0.

\end{minipage}



```
\newpage


# Setup

## Leagues and competitions
This year we played in the following competitions:

```{r ourleagues}
Y.compos %>% filter(ours==TRUE, current==TRUE) %>% select(id = competition_id,
                                                          Name = competition_name, 
                                                          league_id,
                                                          `League Name` = league_name) %>%
  kbl(longtable = T, booktabs = T, row.names = F) %>%
  kable_styling(latex_options = c("repeat_header", "striped", "hold_position"),
                font_size = 7) 
```

In the whole dataset, we have played in leagues with id 
numbers `r F.inningses.us %>% select(league_id) %>% distinct() %>% drop_na() %>%pull()` and
in `r F.inningses.us %>% select(competition_id) %>% distinct() %>% drop_na() %>% nrow()` distinct competitions.

## Players

There are `r nrow(Y.currentplayers %>% filter(player_club==conf$club_of_interest))` recorded
playing for the club this season or last season, and `r nrow(Y.players)` in the whole
dataset.

## Date ranges
Data collected from Play-Cricket. 
For `r conf$club_name`, from `r B.dates$our_earliest` to `r B.dates$our_latest`,
n=`r B.dates$count_us` innings.  For all matches, from `r B.dates$all_earliest` to
`r B.dates$all_latest`, n=`r B.dates$count_all` innings.

# Notes

The underlying dataset is collected from play-cricket, then processed and analysed. This 
report will therefore not include data which are missing from play-cricket, and 
will replicate errors from there. It is not, and cannot be, a complete record.

Records with missing data are interpreted as nicely as feels sensible, but in general are 
simply ignored. This usually results in the exclusion of part-complete data, probably
giving incorrect aggregate or average figures. A very few match scorecards are so 
unreliable that they are excluded.

Many tables presented here are one end of a filtered and sorted dataset. There 
is more interest 
in tops than in bottoms, though both are represented. The underlying data are versatile 
enough to output further, if requested, with appropriate preparation.

No responsibility is taken for any purpose to which this report may be put. It should be 
viewed as mere entertainment, or for scholarly statistical purposes^[which are,
of course, inherently entertaining], and not relied upon as the sole judge of performance.
No assessment of an individual's performance is made or implied. 

_Comment is free, but stats are sacred._
